\begin{thebibliography}{10}

\bibitem{albarghouthi2017probabilistic}
Aws Albarghouthi.
\newblock Probabilistic horn clause verification.
\newblock In {\em International Static Analysis Symposium}, pages 1--22.
  Springer, 2017.

\bibitem{anand2008demand}
Saswat Anand, Patrice Godefroid, and Nikolai Tillmann.
\newblock Demand-driven compositional symbolic execution.
\newblock In {\em International Conference on Tools and Algorithms for the
  Construction and Analysis of Systems}, pages 367--381. Springer, 2008.

\bibitem{avgerinos2014enhancing}
Thanassis Avgerinos, Alexandre Rebert, Sang~Kil Cha, and David Brumley.
\newblock Enhancing symbolic execution with veritesting.
\newblock In {\em Proceedings of the 36th International Conference on Software
  Engineering}, pages 1083--1094. ACM, 2014.

\bibitem{babic2008calysto}
Domagoj Babic and Alan Hu.
\newblock Calysto: Scalable and precise extended static checking.
\newblock In {\em Software Engineering, 2008. ICSE'08. ACM/IEEE 30th
  International Conference on}, pages 211--220. IEEE, 2008.

\bibitem{SurveySymExec-CSUR18}
Roberto Baldoni, Emilio Coppa, Daniele~Cono D'Elia, Camil Demetrescu, and Irene
  Finocchi.
\newblock A survey of symbolic execution techniques.
\newblock {\em ACM Comput. Surv.}, 51(3), 2018.

\bibitem{berdine2007shape}
Josh Berdine, Cristiano Calcagno, Byron Cook, Dino Distefano, Peter~W
  O’hearn, Thomas Wies, and Hongseok Yang.
\newblock Shape analysis for composite data structures.
\newblock In {\em International Conference on Computer Aided Verification},
  pages 178--192. Springer, 2007.

\bibitem{berdine2005symbolic}
Josh Berdine, Cristiano Calcagno, and Peter~W O’hearn.
\newblock Symbolic execution with separation logic.
\newblock In {\em Asian Symposium on Programming Languages and Systems}, pages
  52--68. Springer, 2005.

\bibitem{bjorner2015horn}
Nikolaj Bj{\o}rner, Arie Gurfinkel, Ken McMillan, and Andrey Rybalchenko.
\newblock Horn clause solvers for program verification.
\newblock In {\em Fields of Logic and Computation II}, pages 24--51. Springer,
  2015.

\bibitem{bounimova2013billions}
Ella Bounimova, Patrice Godefroid, and David Molnar.
\newblock Billions and billions of constraints: Whitebox fuzz testing in
  production.
\newblock In {\em Proceedings of the 2013 International Conference on Software
  Engineering}, pages 122--131. IEEE Press, 2013.

\bibitem{calcagno2011infer}
Cristiano Calcagno and Dino Distefano.
\newblock Infer: An automatic program verifier for memory safety of c programs.
\newblock In {\em NASA Formal Methods Symposium}, pages 459--465. Springer,
  2011.

\bibitem{calcagno2011compositional}
Cristiano Calcagno, Dino Distefano, Peter~W O’hearn, and Hongseok Yang.
\newblock Compositional shape analysis by means of bi-abduction.
\newblock {\em Journal of the ACM (JACM)}, 58(6):26, 2011.

\bibitem{cathcart2017higher}
Toby Cathcart~Burn, C-H~Luke Ong, and Steven~J Ramsay.
\newblock Higher-order constrained horn clauses for verification.
\newblock {\em Proceedings of the ACM on Programming Languages}, 2(POPL):11,
  2017.

\bibitem{christakis2015ic}
Maria Christakis and Patrice Godefroid.
\newblock Ic-cut: a compositional search strategy for dynamic test generation.
\newblock In {\em Model Checking Software}, pages 300--318. Springer, 2015.

\bibitem{cousot1977abstract}
Patrick Cousot and Radhia Cousot.
\newblock Abstract interpretation: a unified lattice model for static analysis
  of programs by construction or approximation of fixpoints.
\newblock In {\em Proceedings of the 4th ACM SIGACT-SIGPLAN symposium on
  Principles of programming languages}, pages 238--252. ACM, 1977.

\bibitem{deng2012efficient}
Xianghua Deng, Jooyong Lee, et~al.
\newblock Efficient and formal generalized symbolic execution.
\newblock {\em Automated Software Engineering}, 19(3):233--301, 2012.

\bibitem{dillig2008sound}
Isil Dillig, Thomas Dillig, and Alex Aiken.
\newblock Sound, complete and scalable path-sensitive analysis.
\newblock In {\em ACM SIGPLAN Notices}, volume~43, pages 270--280. ACM, 2008.

\bibitem{distefano2009attacking}
Dino Distefano.
\newblock Attacking large industrial code with bi-abductive inference.
\newblock In {\em International Workshop on Formal Methods for Industrial
  Critical Systems}, pages 1--8. Springer, 2009.

\bibitem{distefano2008jstar}
Dino Distefano and Matthew~J Parkinson~J.
\newblock jstar: Towards practical verification for java.
\newblock In {\em ACM Sigplan Notices}, volume~43, pages 213--226. ACM, 2008.

\bibitem{dudka2013byte}
Kamil Dudka, Petr Peringer, and Tom{\'a}{\v{s}} Vojnar.
\newblock Byte-precise verification of low-level list manipulation.
\newblock In {\em International Static Analysis Symposium}, pages 215--237.
  Springer, 2013.

\bibitem{fedyukovich2017sampling}
Grigory Fedyukovich, Samuel~J Kaufman, and Rastislav Bod{\'\i}k.
\newblock Sampling invariants from frequency distributions.
\newblock In {\em Proceedings of the 17th Conference on Formal Methods in
  Computer-Aided Design}, pages 100--107. FMCAD Inc, 2017.

\bibitem{godefroid2007compositional}
Patrice Godefroid.
\newblock Compositional dynamic test generation.
\newblock In {\em ACM Sigplan Notices}, volume~42, pages 47--54. ACM, 2007.

\bibitem{godefroid2005dart}
Patrice Godefroid, Nils Klarlund, and Koushik Sen.
\newblock Dart: Directed automated random testing.
\newblock In {\em ACM Sigplan Notices}, volume~40, pages 213--223. ACM, 2005.

\bibitem{grebenshchikov2012hsf}
Sergey Grebenshchikov, Ashutosh Gupta, Nuno~P Lopes, Corneliu Popeea, and
  Andrey Rybalchenko.
\newblock Hsf (c): A software verifier based on horn clauses.
\newblock In {\em International Conference on Tools and Algorithms for the
  Construction and Analysis of Systems}, pages 549--551. Springer, 2012.

\bibitem{gurfinkel2015seahorn}
Arie Gurfinkel, Temesghen Kahsai, Anvesh Komuravelli, and Jorge~A Navas.
\newblock The seahorn verification framework.
\newblock In {\em International Conference on Computer Aided Verification},
  pages 343--361. Springer, 2015.

\bibitem{gurfinkel2017context}
Arie Gurfinkel and Jorge~A Navas.
\newblock A context-sensitive memory model for verification of c/c++ programs.
\newblock In {\em International Static Analysis Symposium}, pages 148--168.
  Springer, 2017.

\bibitem{hoder2012generalized}
Kry{\v{s}}tof Hoder and Nikolaj Bj{\o}rner.
\newblock Generalized property directed reachability.
\newblock In {\em International Conference on Theory and Applications of
  Satisfiability Testing}, pages 157--171. Springer, 2012.

\bibitem{hojjat2012verification}
Hossein Hojjat, Filip Kone{\v{c}}n{\`y}, Florent Garnier, Radu Iosif, Viktor
  Kuncak, and Philipp R{\"u}mmer.
\newblock A verification toolkit for numerical transition systems.
\newblock In {\em International Symposium on Formal Methods}, pages 247--251.
  Springer, 2012.

\bibitem{kafle2016solving}
Bishoksan Kafle, John~P Gallagher, and Pierre Ganty.
\newblock Solving non-linear horn clauses using a linear horn clause solver.
\newblock {\em arXiv preprint arXiv:1607.04459}, 2016.

\bibitem{kahsai2017quantified}
Temesghen Kahsai, Rody Kersten, Philipp R{\"u}mmer, and Martin Sch{\"a}f.
\newblock Quantified heap invariants for object-oriented programs.
\newblock In {\em Logic for Programming, Artificial Intelligence and
  Reasoning}, pages 368--384, 2017.

\bibitem{kahsai2016jayhorn}
Temesghen Kahsai, Philipp R{\"u}mmer, Huascar Sanchez, and Martin Sch{\"a}f.
\newblock Jayhorn: A framework for verifying java programs.
\newblock In {\em International Conference on Computer Aided Verification},
  pages 352--358. Springer, Cham, 2016.

\bibitem{khurshid2003generalized}
Sarfraz Khurshid, Corina~S P{\u{a}}s{\u{a}}reanu, and Willem Visser.
\newblock Generalized symbolic execution for model checking and testing.
\newblock In {\em International Conference on Tools and Algorithms for the
  Construction and Analysis of Systems}, pages 553--568. Springer, 2003.

\bibitem{koelbl2005constructing}
Alfred Koelbl and Carl Pixley.
\newblock Constructing efficient formal models from high-level descriptions
  using symbolic simulation.
\newblock {\em International Journal of Parallel Programming}, 33(6):645--666,
  2005.

\bibitem{komuravelli2016smt}
Anvesh Komuravelli, Arie Gurfinkel, and Sagar Chaki.
\newblock Smt-based model checking for recursive programs.
\newblock {\em Formal Methods in System Design}, 48(3):175--205, 2016.

\bibitem{kuznetsov2012efficient}
Volodymyr Kuznetsov, Johannes Kinder, Stefan Bucur, and George Candea.
\newblock Efficient state merging in symbolic execution.
\newblock {\em Acm Sigplan Notices}, 47(6):193--204, 2012.

\bibitem{lin2016compositional}
Yude Lin, Tim Miller, and Harald S{\o}ndergaard.
\newblock Compositional symbolic execution: Incremental solving revisited.
\newblock In {\em Software Engineering Conference (APSEC), 2016 23rd
  Asia-Pacific}, pages 273--280. IEEE, 2016.

\bibitem{mcmillan2013computing}
Kenneth McMillan and Andrey Rybalchenko.
\newblock Computing relational fixed points using interpolation.
\newblock {\em Technical report, Technical report, 2012}, 2013.

\bibitem{reynolds2002separation}
John~C Reynolds.
\newblock Separation logic: A logic for shared mutable data structures.
\newblock In {\em Logic in Computer Science, 2002. Proceedings. 17th Annual
  IEEE Symposium on}, pages 55--74. IEEE, 2002.

\bibitem{slaby2013compact}
Jiri Slaby, Jan Strej{\v{c}}ek, and Marek Trt{\'\i}k.
\newblock Compact symbolic execution.
\newblock In {\em International Symposium on Automated Technology for
  Verification and Analysis}, pages 193--207. Springer, 2013.

\bibitem{tillmann2008pex}
Nikolai Tillmann and Jonathan De~Halleux.
\newblock Pex --- white box test generation for .net.
\newblock In {\em International conference on tests and proofs}, pages
  134--153. Springer, 2008.

\bibitem{torlak2014lightweight}
Emina Torlak and Rastislav Bodik.
\newblock A lightweight symbolic virtual machine for solver-aided host
  languages.
\newblock In {\em ACM SIGPLAN Notices}, volume~49, pages 530--541. ACM, 2014.

\bibitem{unno2013automating}
Hiroshi Unno, Tachio Terauchi, and Naoki Kobayashi.
\newblock Automating relatively complete verification of higher-order
  functional programs.
\newblock {\em ACM SIGPLAN Notices}, 48(1):75--86, 2013.

\bibitem{vazou2015bounded}
Niki Vazou, Alexander Bakst, and Ranjit Jhala.
\newblock Bounded refinement types.
\newblock In {\em ACM SIGPLAN Notices}, volume~50, pages 48--61. ACM, 2015.

\bibitem{xie2016proteus}
Xiaofei Xie, Bihuan Chen, Yang Liu, Wei Le, and Xiaohong Li.
\newblock Proteus: Computing disjunctive loop summary via path dependency
  analysis.
\newblock In {\em Proceedings of the 2016 24th ACM SIGSOFT International
  Symposium on Foundations of Software Engineering}, pages 61--72. ACM, 2016.

\bibitem{xie2005scalable}
Yichen Xie and Alex Aiken.
\newblock Scalable error detection using boolean satisfiability.
\newblock {\em Acm Sigplan Notices}, 40(1):351--363, 2005.

\bibitem{zhu2013compositional}
He~Zhu and Suresh Jagannathan.
\newblock Compositional and lightweight dependent type inference for ml.
\newblock In {\em International Workshop on Verification, Model Checking, and
  Abstract Interpretation}, pages 295--314. Springer, 2013.

\bibitem{zhu2018data}
He~Zhu, Stephen Magill, and Suresh Jagannathan.
\newblock A data-driven chc solver.
\newblock In {\em Proceedings of the 39th ACM SIGPLAN Conference on Programming
  Language Design and Implementation}, pages 707--721. ACM, 2018.

\end{thebibliography}
