\begin{thebibliography}{10}
\def\selectlanguageifdefined#1{
\expandafter\ifx\csname date#1\endcsname\relax
\else\selectlanguage{#1}\fi}
\providecommand*{\href}[2]{{\small #2}}
\providecommand*{\url}[1]{{\small #1}}
\providecommand*{\BibUrl}[1]{\url{#1}}
\providecommand{\BibAnnote}[1]{}
\providecommand*{\BibEmph}[1]{#1}
\ProvideTextCommandDefault{\cyrdash}{\iflanguage{russian}{\hbox
  to.8em{--\hss--}}{\textemdash}}
\providecommand*{\BibDash}{\ifdim\lastskip>0pt\unskip\nobreak\hskip.2em plus
  0.1em\fi
\cyrdash\hskip.2em plus 0.1em\ignorespaces}
\renewcommand{\newblock}{\ignorespaces}

\bibitem{Azimov:2018:CPQ:3210259.3210264}
\selectlanguageifdefined{english}
\BibEmph{Azimov~Rustam, Grigorev~Semyon}.
  \href{http://dx.doi.org/10.1145/3210259.3210264}{Context-free Path Querying
  by Matrix Multiplication}~// Proceedings of the 1st ACM SIGMOD Joint
  International Workshop on Graph Data Management Experiences \& Systems
  (GRADES) and Network Data Analytics (NDA). \BibDash
\newblock GRADES-NDA '18. \BibDash
\newblock New York, NY, USA~: ACM, 2018. \BibDash
\newblock P.~5:1--5:10. \BibDash
\newblock Access mode: \BibUrl{http://doi.acm.org/10.1145/3210259.3210264}.

\bibitem{EddyDurbin}
  \selectlanguageifdefined{english}
  \BibEmph{Richard~Durbin, Sean~R~Eddy, Anders~Krogh, Graeme~Mitchison}.
Biological sequence analysis: probabilistic models of proteins and nucleic
  acids. \BibDash
\newblock Cambridge university press, 1998.

\bibitem{dowell2004rna}
\selectlanguageifdefined{english}
\BibEmph{Dowell~Robin~D}. RNA structural alignment using stochastic
  context-free grammars. \BibDash
\newblock Washington University, 2004.

\bibitem{LWPCFG}
\selectlanguageifdefined{english}
\BibEmph{Dowell~Robin~D, Eddy~Sean~R}. Evaluation of several lightweight
  stochastic context-free grammars for RNA secondary structure prediction~//
  \BibEmph{BMC bioinformatics}. \BibDash
\newblock 2004. \BibDash
\newblock Vol.~5, no.~1. \BibDash
\newblock P.~71.

\bibitem{trnadb1}
\selectlanguageifdefined{english}
Genomic tRNA Database [Online]. \BibDash
\newblock Access mode: \BibUrl{http://gtrnadb2009.ucsc.edu/} (online; accessed:
  05.05.2019).

\bibitem{ghosh1999study}
\selectlanguageifdefined{english}
\BibEmph{Ghosh~Anup~K, Schwartzbard~Aaron}. A Study in Using Neural Networks
  for Anomaly and Misuse Detection.~// USENIX security symposium. \BibDash
\newblock Vol.~99. \BibDash
\newblock 1999. \BibDash
\newblock P.~12.

\bibitem{hmmer}
\selectlanguageifdefined{english}
HMMER [Online]. \BibDash
\newblock Access mode: \BibUrl{http://hmmer.org/} (online; accessed:
  05.05.2019).

\bibitem{ANN}
\selectlanguageifdefined{english}
\BibEmph{Higashi~Susan, Hungria~Mariangela, Brunetto~MADC}. Bacteria
  classification based on 16S ribosomal gene using artificial neural
  networks~// Proceedings of the 8th WSEAS International Conference on
  Computational intelligence, man-machine systems and cybernetics. \BibDash
\newblock 2009. \BibDash
\newblock P.~86--91.

\bibitem{hofmeyr1998intrusion}
\selectlanguageifdefined{english}
\BibEmph{Hofmeyr~Steven~A, Forrest~Stephanie, Somayaji~Anil}. Intrusion
  detection using sequences of system calls~// \BibEmph{Journal of computer
  security}. \BibDash
\newblock 1998. \BibDash
\newblock Vol.~6, no.~3. \BibDash
\newblock P.~151--180.

\bibitem{infernal}
\selectlanguageifdefined{english}
Infernal [Online]. \BibDash
\newblock Access mode: \BibUrl{http://eddylab.org/infernal/} (online; accessed:
  05.05.2019).

\bibitem{jetbrains}
\selectlanguageifdefined{english}
JetBrains Programming Languages and Tools Lab [Online]. \BibDash
\newblock Access mode: \BibUrl{https://research.jetbrains.org/groups/plt_lab}
  (online; accessed: 05.05.2019).

\bibitem{keras}
\selectlanguageifdefined{english}
Keras [Online]. \BibDash
\newblock Access mode: \BibUrl{https://keras.io/} (online; accessed:
  08.05.2019).

\bibitem{PCFG}
\selectlanguageifdefined{english}
\BibEmph{Knudsen~Bjarne, Hein~Jotun}. RNA secondary structure prediction using
  stochastic context-free grammars and evolutionary history~//
  \BibEmph{Bioinformatics (Oxford, England)}. \BibDash
\newblock 1999. \BibDash
\newblock Vol.~15, no.~6. \BibDash
\newblock P.~446--454.

\bibitem{miladi2017rnascclust}
  \selectlanguageifdefined{english}
  \BibEmph{Milad~Miladi, Alexander~Junge, Fabrizio~Costa et~al.}
RNAscClust: clustering RNA sequences using structure conservation and graph
  based motifs //
  \BibEmph{Bioinformatics}. \BibDash
\newblock 2017. \BibDash
\newblock Vol.~33, no.~14. \BibDash
\newblock P.~2089--2096.

\bibitem{GrammarsRNA}
\selectlanguageifdefined{english}
\BibEmph{Rivas~Elena, Eddy~Sean~R}. The language of RNA: a formal grammar that
  includes pseudoknots~// \BibEmph{Bioinformatics}. \BibDash
\newblock 2000. \BibDash
\newblock Vol.~16, no.~4. \BibDash
\newblock P.~334--340.

\bibitem{Humidor}
\selectlanguageifdefined{english}
\BibEmph{Sherman~Douglas}. Humidor: Microbial Community Classification of the
  16S Gene by Training CIGAR Strings with Convolutional Neural Networks.
  \BibDash
\newblock 2017.

\bibitem{tensorflow}
\selectlanguageifdefined{english}
TensorFlow [Online]. \BibDash
\newblock Access mode: \BibUrl{https://www.tensorflow.org/} (online; accessed:
  08.05.2019).

\bibitem{vrehakova2014variation}
  \selectlanguageifdefined{english}
  \BibEmph{Kl{\'a}ra~{\v{R}}eh{\'a}kov{\'a},
  Jeffrey~R~Johansen, Mary~B~Bowen et~al}.
Variation in secondary structure of the 16S rRNA molecule in cyanobacteria with
  implications for phylogenetic analysis // \BibEmph{Fottea}. \BibDash
\newblock 2014. \BibDash
\newblock Vol.~14. \BibDash
\newblock P.~161--178.

\bibitem{wespi2000intrusion}
\selectlanguageifdefined{english}
\BibEmph{Wespi~Andreas, Dacier~Marc, Debar~Herv{\'e}}. Intrusion detection
  using variable-length audit trail patterns~// International Workshop on
  Recent Advances in Intrusion Detection~/ Springer. \BibDash
\newblock 2000. \BibDash
\newblock P.~110--129.

\bibitem{yacc}
\selectlanguageifdefined{english}
YaccConstructor [Online]. \BibDash
\newblock Access mode: \BibUrl{https://github.com/YaccConstructor} (online;
  accessed: 05.05.2019).

\bibitem{trnadb2}
\selectlanguageifdefined{english}
tRNADB-CE [Online]. \BibDash
\newblock Access mode:
  \BibUrl{http://trna.ie.niigata-u.ac.jp/cgi-bin/trnadb/index.cgi} (online;
  accessed: 05.05.2019).

\bibitem{baklanovsk2015}
\selectlanguageifdefined{russian}
\BibEmph{Баклановский~М.~В.,
  Ханов~А.~Р.} Поведенческая
  идентификация программ~//
  \BibEmph{Моделирование и анализ
  информационных систем}. \BibDash
\newblock 2015. \BibDash
\newblock Vol.~21, no.~6. \BibDash
\newblock P.~120--130.

\bibitem{baklanovsk2016}
  \selectlanguageifdefined{russian}
  \BibEmph{Баклановский~М.~В., Ханов~А.~Р., Комаров~К.~М.,
  Лозов~П.~А.}
Оценка точности алгоритма распознавания
  вредоносных программ на основе поиска
  аномалий в работе процессов // \BibEmph{Научно-технический
  вестник информационных технологий,
  механики и оптики}. \BibDash
\newblock 2016. \BibDash
\newblock Vol.~16, no.~5.

\end{thebibliography}
