\begin{thebibliography}{10}
\def\selectlanguageifdefined#1{
\expandafter\ifx\csname date#1\endcsname\relax
\else\selectlanguage{#1}\fi}
\providecommand*{\href}[2]{{\small #2}}
\providecommand*{\url}[1]{{\small #1}}
\providecommand*{\BibUrl}[1]{\url{#1}}
\providecommand{\BibAnnote}[1]{}
\providecommand*{\BibEmph}[1]{#1}
\ProvideTextCommandDefault{\cyrdash}{\iflanguage{russian}{\hbox
  to.8em{--\hss--}}{\textemdash}}
\providecommand*{\BibDash}{\ifdim\lastskip>0pt\unskip\nobreak\hskip.2em plus
  0.1em\fi
\cyrdash\hskip.2em plus 0.1em\ignorespaces}
\renewcommand{\newblock}{\ignorespaces}

\bibitem{M4RI}
\selectlanguageifdefined{english}
\BibEmph{Albrecht~Martin, Bard~Gregory}. \BibDash
\newblock {The M4RI Library}. \BibDash
\newblock The M4RI~Team, 2019. \BibDash
\newblock Access mode: \BibUrl{https://bitbucket.org/malb/m4ri}.

\bibitem{albrechtefficient}
\selectlanguageifdefined{english}
\BibEmph{Albrecht~MR, Bard~GV, Hart~W}. Efficient multiplication of dense
  matrices over GF (2)~// \BibEmph{arXiv preprint arXiv:0811.1714}. \BibDash
\newblock 2008.

\bibitem{durbin1996biological}
  \selectlanguageifdefined{english}
  \BibEmph{Richard~Durbin, Sean~Eddy, Anders~Krogh,
  G~Mitchison}.
Biological sequence analysis  \BibDash
\newblock Cambridge University Press, 1996.

\bibitem{dowell2004evaluation}
\selectlanguageifdefined{english}
\BibEmph{Dowell~Robin~D, Eddy~Sean~R}. Evaluation of several lightweight
  stochastic context-free grammars for RNA secondary structure prediction~//
  \BibEmph{BMC bioinformatics}. \BibDash
\newblock 2004. \BibDash
\newblock Vol.~5, no.~1. \BibDash
\newblock P.~71.

\bibitem{bioinformatics19}
\selectlanguageifdefined{english}
\BibEmph{Grigorev.~Semyon, Lunina.~Polina}.
  \href{http://dx.doi.org/10.5220/0007472302340241}{The Composition of Dense
  Neural Networks and Formal Grammars for Secondary Structure Analysis}~//
  Proceedings of the 12th International Joint Conference on Biomedical
  Engineering Systems and Technologies - Volume 3: BIOINFORMATICS,~/ INSTICC.
  \BibDash
\newblock SciTePress, 2019. \BibDash
\newblock P.~234--241.

\bibitem{hopcroft1969formal}
\selectlanguageifdefined{english}
\BibEmph{Hopcroft~John~E, Ullman~Jeffrey~D}. Formal languages and their
  relation to automata. \BibDash
\newblock 1969.

\bibitem{jetbrains}
\selectlanguageifdefined{russian}
JetBrains Programming Languages and Tools Lab [Электронный
  ресурс]. \BibDash
\newblock Access mode: \BibUrl{https://research.jetbrains.org/groups/plt_lab}
  (online; accessed: 05.05.2019).

\bibitem{kasami1966efficient}
\selectlanguageifdefined{english}
\BibEmph{Kasami~Tadao}. An efficient recognition and syntax-analysis algorithm
  for context-free languages~// \BibEmph{Coordinated Science Laboratory Report
  no. R-257}. \BibDash
\newblock 1966.

\bibitem{knudsen1999rna}
\selectlanguageifdefined{english}
\BibEmph{Knudsen~Bjarne, Hein~Jotun}. RNA secondary structure prediction using
  stochastic context-free grammars and evolutionary history.~//
  \BibEmph{Bioinformatics (Oxford, England)}. \BibDash
\newblock 1999. \BibDash
\newblock Vol.~15, no.~6. \BibDash
\newblock P.~446--454.

\bibitem{liu2005parallel}
\selectlanguageifdefined{english}
\BibEmph{Liu~Tong, Schmidt~Bertil}. Parallel RNA secondary structure prediction
  using stochastic context-free grammars~// \BibEmph{Concurrency and
  Computation: Practice and Experience}. \BibDash
\newblock 2005. \BibDash
\newblock Vol.~17, no.~14. \BibDash
\newblock P.~1669--1685.

\bibitem{nvidia2011nvidia}
\selectlanguageifdefined{english}
\BibEmph{Nvidia~CUDA}. Nvidia cuda c programming guide~// \BibEmph{Nvidia
  Corporation}. \BibDash
\newblock 2011. \BibDash
\newblock Vol. 120, no.~18. \BibDash
\newblock P.~8.

\bibitem{Okhotin:2014:PMM:2565359.2565379}
\selectlanguageifdefined{english}
\BibEmph{Okhotin~Alexander}. Parsing by Matrix Multiplication Generalized to
  Boolean Grammars~// \BibEmph{Theor. Comput. Sci.} \BibDash
\newblock 2014. \BibDash Jan. \BibDash
\newblock Vol. 516. \BibDash
\newblock P.~101--120. \BibDash
\newblock Access mode: \BibUrl{http://dx.doi.org/10.1016/j.tcs.2013.09.011}.

\bibitem{arlazarov1970economical}
  \selectlanguageifdefined{english}
  \BibEmph{Vladimir~L'vovich~Arlazarov, Yefim~A~Dinitz, MA~Kronrod,
  IgorAleksandrovich~Faradzhev}.
On economical construction of the transitive closure of an oriented graph~//
   Doklady Akademii Nauk~// Russian Academy of
  Sciences. \BibDash
\newblock Vol.~194. \BibDash
\newblock 1970. \BibDash
\newblock P.~487--488.

\bibitem{rivas2000language}
\selectlanguageifdefined{english}
\BibEmph{Rivas~Elena, Eddy~Sean~R}. The language of RNA: a formal grammar that
  includes pseudoknots~// \BibEmph{Bioinformatics}. \BibDash
\newblock 2000. \BibDash
\newblock Vol.~16, no.~4. \BibDash
\newblock P.~334--340.

\bibitem{Valiant:1975:GCR:1739932.1740048}
\selectlanguageifdefined{english}
\BibEmph{Valiant~Leslie~G.} General Context-free Recognition in Less Than Cubic
  Time~// \BibEmph{J. Comput. Syst. Sci.} \BibDash
\newblock 1975. \BibDash Apr. \BibDash
\newblock Vol.~10, no.~2. \BibDash
\newblock P.~308--315. \BibDash
\newblock Access mode:
  \BibUrl{http://dx.doi.org/10.1016/S0022-0000(75)80046-8}.

\bibitem{Younger:1966:CLP:1441427.1442019}
\selectlanguageifdefined{english}
\BibEmph{Younger~Daniel~H.} Context-free Language Processing in Time N3~//
  Proceedings of the 7th Annual Symposium on Switching and Automata Theory
  (Swat 1966). \BibDash
\newblock SWAT '66. \BibDash
\newblock Washington, DC, USA~: IEEE Computer Society, 1966. \BibDash
\newblock P.~7--20. \BibDash
\newblock Access mode: \BibUrl{https://doi.org/10.1109/SWAT.1966.7}.

\bibitem{zier2013rna}
\selectlanguageifdefined{english}
\BibEmph{Zier-Vogel~Ryan, Domaratzki~Michael}. RNA pseudoknot prediction
  through stochastic conjunctive grammars~// \BibEmph{Computability in Europe
  2013. Informal Proceedings}. \BibDash
\newblock 2013. \BibDash
\newblock P.~80--89.

\bibitem{alg}
\selectlanguageifdefined{russian}
\BibEmph{Явейн~А.} Разработка алгоритма
  синтаксического анализа через умножение
  матриц. \BibDash
\newblock Access mode:
  \BibUrl{https://github.com/YaccConstructor/articles/blob/master/InProgress/Yaveyn_alg/jbalg.pdf}
  (online; accessed: 13.05.2018).

\end{thebibliography}
