\title{Разработка транслятора из реляционного языка программирования в функциональный}
\titlerunning{Транслятора реляционного языка в функциональный}

\author{Артемьева Ирина}
\authorrunning{Артемьева И.}

\tocauthor{Артемьева И.}
\institute{Национальный исследовательский университет ИТМО\\
	\email{irina-pluralia@rambler.ru}}

\maketitle

\lstdefinestyle{mycode}{
  belowcaptionskip=1\baselineskip,
  breaklines=true,
  xleftmargin=\parindent,
  showstringspaces=false,
  basicstyle=\footnotesize\ttfamily,
  keywordstyle=\bfseries,
  commentstyle=\itshape\color{gray!40!black},
  stringstyle=\color{red},
  numbers=left,
  numbersep=5pt,
  numberstyle=\tiny\color{gray},
}
\lstset{escapechar=@,style=mycode}

\newcommand{\miniKanren}{\textsc{miniKanren}}
\newcommand{\microKanren}{\textsc{microKanren}}
\newcommand{\mercury}{\textsc{Mercury}}
\newcommand{\haskell}{\textsc{Haskell}}
\newcommand{\prolog}{\textsc{Prolog}}
\newcommand{\scheme}{\textsc{Scheme}}
\newcommand{\logen}{\textsc{LOGEN}}
\newcommand{\ocanren}{\textsc{OCanren}}
\newcommand{\curry}{\textsc{Curry}}
\newcommand{\github}{\textsc{GitHub}}
\lstset{mathescape=true}

\newcommand{\fromkw}{\textbf{\textit{from}}}
\newcommand{\andkw}{\textbf{\textit{and}}}
\newcommand{\returnkw}{\textbf{return}}
\algrenewcommand\algorithmicindent{1.em}

\graphicspath{{Artemeva/}}

\algnewcommand\algorithmicotherwise{\textbf{otherwise}}
\algrenewcommand\algorithmicreturn{\textbf{return}}

\algdef{SE}[RETURN]{Return}{EndReturn}[1]{\algorithmicreturn\ #1}{\algorithmicend| \algorithmicreturn}

\algdef{SE}[OTHERWISE]{Otherwise}{EndOtherwise}[0]{\algorithmicotherwise\ \algorithmicdo}{\algorithmicend \algoorithmicotherwise}
\algtext*{EndOtherwise}%
\algtext*{EndReturn}%
\algtext*{EndSwitch}%
\algtext*{EndCase}%

% \newtheorem{theorem}{Утверждение}

\input{Artemeva/contents/intro}

\input{Artemeva/contents/chapter1/main}
\input{Artemeva/contents/chapter2/main}
\input{Artemeva/contents/chapter3/main}
\input{Artemeva/contents/chapter4/main}
\input{Artemeva/contents/chapter5/main}

\input{Artemeva/contents/outro}

\begin{thebibliography}{10}
  \def\selectlanguageifdefined#1{
  \expandafter\ifx\csname date#1\endcsname\relax
  \else\selectlanguage{#1}\fi}
  \providecommand*{\href}[2]{{\small #2}}
  \providecommand*{\url}[1]{{\small #1}}
  \providecommand*{\BibUrl}[1]{\url{#1}}
  \providecommand{\BibAnnote}[1]{}
  \providecommand*{\BibEmph}[1]{#1}
  \ProvideTextCommandDefault{\cyrdash}{\iflanguage{russian}{\hbox
    to.8em{--\hss--}}{\textemdash}}
  \providecommand*{\BibDash}{\ifdim\lastskip>0pt\unskip\nobreak\hskip.2em plus
    0.1em\fi
  \cyrdash\hskip.2em plus 0.1em\ignorespaces}
  \renewcommand{\newblock}{\ignorespaces}

  \bibitem{kiselyov2005bit}
  \selectlanguageifdefined{english}
  Backtracking, Interleaving, and Terminating Monad Transformers: (Functional
    Pearl)~/ Oleg~Kiselyov, Chung-chieh~Shan, Daniel~P.~Friedman, Amr~Sabry~//
    \BibEmph{SIGPLAN Not.} \BibDash
  \newblock 2005. \BibDash Sep. \BibDash
  \newblock Vol.~40. \BibDash
  \newblock P.~192–203.

  \bibitem{Bellia1986TRB}
  \selectlanguageifdefined{english}
  \BibEmph{Bellia~Marco, Levi~Giorgio}. The relation between logic and functional
    languages: a survey~// \BibEmph{The Journal of Logic Programming}. \BibDash
  \newblock 1986. \BibDash
  \newblock Vol.~3, no.~3. \BibDash
  \newblock P.~217 -- 236.

  \bibitem{Brassel2008FFL}
  \selectlanguageifdefined{english}
  \BibEmph{Brassel~Bernd, Fischer~Sebastian}. From Functional Logic Programs to
    Purely Functional Programs Preserving Laziness. \BibDash
  \newblock Vol.~5836. \BibDash
  \newblock 2008. \BibDash 09. \BibDash
  \newblock P.~25--42.

  \bibitem{Byrd2009RPM}
  \selectlanguageifdefined{english}
  \BibEmph{Byrd~William}. Relational Programming in miniKanren: Techniques,
    Applications, and Implementations. \BibDash
  \newblock 2009. \BibDash 09.

  \bibitem{Friedman2005TRS}
  \selectlanguageifdefined{english}
  \BibEmph{Friedman~Daniel~P., Byrd~William~E., Kiselyov~Oleg}. The Reasoned
    Schemer. \BibDash
  \newblock The MIT Press, 2005.

  \bibitem{Hanus2012SSF}
  \selectlanguageifdefined{english}
  \BibEmph{Hanus~M., Peem{\"o}ller~B., Reck~F.} Search Strategies for Functional
    Logic Programming~// Proc. of the 5th Working Conference on Programming
    Languages (ATPS'12). \BibDash
  \newblock Springer LNI 199, 2012. \BibDash
  \newblock P.~61--74.

  \bibitem{Hanus2016CIF}
  \selectlanguageifdefined{english}
  \BibEmph{Hanus~Michael~(ed.)}. Curry: An Integrated Functional Logic Language.
    \BibDash
  \newblock 2016. \BibDash
  \newblock Access mode:
    \BibUrl{https://web.cecs.pdx.edu/~antoy/Courses/TPFLP/report.pdf}.

  \bibitem{hemann2013ukanren}
  \selectlanguageifdefined{english}
  \BibEmph{Hemann~Jason, Friedman~Daniel~P.} uKanren: A Minimal Functional Core
    for Relational Programming. \BibDash
  \newblock 2013.

  \bibitem{jones1993partial}
  \selectlanguageifdefined{english}
  \BibEmph{Jones~Neil~D, Gomard~Carsten~K, Sestoft~Peter}. Partial evaluation and
    automatic program generation. \BibDash
  \newblock Peter Sestoft, 1993.

  \bibitem{Jones2003HHH}
  \selectlanguageifdefined{english}
  \BibEmph{Jones~S. Peyton~(ed.)}. Haskell 98 Language and Libraries --- The
    Revised Report. \BibDash
  \newblock 2003. \BibDash
  \newblock Access mode: \BibUrl{https://www.haskell.org/onlinereport/}.

  \bibitem{Bernd2011FCL}
  \selectlanguageifdefined{english}
  KiCS2: A New Compiler from Curry to Haskell~/ Bernd~Bra{\ss}el, Michael~Hanus,
    Bj{\"o}rn~Peem{\"o}ller, Fabian~Reck~// Functional and Constraint Logic
    Programming. \BibDash
  \newblock Springer Berlin Heidelberg, 2011. \BibDash
  \newblock P.~1--18.

  \bibitem{Kosarev2018TER}
  \selectlanguageifdefined{english}
  \BibEmph{Kosarev~Dmitrii, Boulytchev~Dmitri}. Typed Embedding of a Relational
    Language in OCaml~// \BibEmph{Electronic Proceedings in Theoretical Computer
    Science}. \BibDash
  \newblock 2018. \BibDash 12. \BibDash
  \newblock Vol. 285. \BibDash
  \newblock P.~1--22.

  \bibitem{Lin1997ASC}
  \selectlanguageifdefined{english}
  \BibEmph{Lin~Fangzhen}. Applications of the Situation Calculus To Formalizing
    Control and Strategic Information: The Prolog Cut Operator~//
    \BibEmph{Artificial Intelligence}. \BibDash
  \newblock 1997. \BibDash 11. \BibDash
  \newblock Vol. 103.

  \bibitem{Lipovaca2011LYAH}
  \selectlanguageifdefined{english}
  \BibEmph{Lipovaca~Miran}. Learn You a Haskell for Great Good! A Beginner’s
    Guide. \BibDash
  \newblock No Starch Press, 2011.

  \bibitem{lozov2019relational}
  \selectlanguageifdefined{english}
  \BibEmph{Lozov~Petr, Verbitskaia~Ekaterina, Boulytchev~Dmitry}. Relational
    Interpreters for Search Problems~// Relational Programming Workshop. \BibDash
  \newblock 2019. \BibDash
  \newblock P.~43.

  \bibitem{MacLennan1981IRP}
  \selectlanguageifdefined{english}
  \BibEmph{MacLennan~Bruce~J.} Introduction to relational programming. \BibDash
  \newblock 1981.

  \bibitem{Malpas1987prolog}
  \selectlanguageifdefined{english}
  \BibEmph{Malpas~J.} Prolog: A Relational Language and Its Applications.
    Prentice-Hall international editions. \BibDash
  \newblock Prentice-Hall, 1987.

  \bibitem{Marchiori1995the}
  \selectlanguageifdefined{english}
  \BibEmph{Marchiori~Massimo}. The functional side of logic programming~//
    \BibEmph{FPCA}. \BibDash
  \newblock 1995. \BibDash
  \newblock P.~55--65.

  \bibitem{Matsushita1997FCO}
  \selectlanguageifdefined{english}
  \BibEmph{Matsushita~Tatsuru, Runciman~Colin}. Functional Counterparts of some
    Logic Programming Techniques. \BibDash
  \newblock 1997.

  \bibitem{Nadathur1988OLP}
  \selectlanguageifdefined{english}
  \BibEmph{Nadathur~Gopalan, Miller~Dale}. An Overview of Lambda-Prolog. \BibDash
  \newblock 1988. \BibDash 06. \BibDash
  \newblock P.~810--827.

  \bibitem{Nerode1998LFA}
  \selectlanguageifdefined{english}
  \BibEmph{Nerode~Anil, A.~Shore~Richard}. Logic for Applications~// \BibEmph{J.
    of Logic, Lang. and Inf.} \BibDash
  \newblock 1998. \BibDash Apr. \BibDash
  \newblock Vol.~7. \BibDash
  \newblock P.~228–229.

  \bibitem{rozplokhas2019certified}
  \selectlanguageifdefined{english}
  \BibEmph{Rozplokhas~Dmitry, Vyatkin~Andrey, Boulytchev~Dmitry}. Certified
    Semantics for miniKanren~// miniKanren and Relational Programming Workshop.
    \BibDash
  \newblock 2019. \BibDash
  \newblock P.~80.

  \bibitem{Wielemaker2012TPL}
  \selectlanguageifdefined{english}
  SWI-Prolog~/ Jan~Wielemaker, Tom~Schrijvers, Markus~Triska, Torbjörn~Lager~//
    \BibEmph{Theory and Practice of Logic Programming}. \BibDash
  \newblock 2012. \BibDash
  \newblock Vol.~12, no. 1-2. \BibDash
  \newblock P.~67–96.

  \bibitem{SOMOGYI199617}
  \selectlanguageifdefined{english}
  \BibEmph{Somogyi~Zoltan, Henderson~Fergus, Conway~Thomas}. The execution
    algorithm of mercury, an efficient purely declarative logic programming
    language~// \BibEmph{The Journal of Logic Programming}. \BibDash
  \newblock 1996. \BibDash
  \newblock Vol.~29. \BibDash
  \newblock P.~17 -- 64.

  \bibitem{leuschel2004prolog}
  \selectlanguageifdefined{english}
  \href{http://dx.doi.org/10.1007/978-3-540-25951-0_11}{Specialising Interpreters
    Using Offline Partial Deduction}~/ Michael~Leuschel, Stephen-John~Craig,
    Maurice~Bruynooghe, Wim~Vanhoof. \BibDash
  \newblock Vol.~3049. \BibDash
  \newblock 2004. \BibDash 01. \BibDash
  \newblock P.~340--375.

  \bibitem{Swift2012XSB}
  \selectlanguageifdefined{english}
  \BibEmph{Swift~Terrance, Warren~David~S.} XSB: Extending Prolog with tabled
    logic programming~// \BibEmph{Theory and Practice of Logic Programming}.
    \BibDash
  \newblock 2012. \BibDash Jan. \BibDash
  \newblock Vol.~12. \BibDash
  \newblock P.~157--187.

  \bibitem{Thiemann1997AUF}
  \selectlanguageifdefined{english}
  \BibEmph{Thiemann~Peter}. A Unified Framework for Binding-Time Analysis~//
    TAPSOFT. \BibDash
  \newblock 1997.

  \bibitem{byrd2017unified}
  \selectlanguageifdefined{english}
  A Unified Approach to Solving Seven Programming Problems (Functional Pearl)~/
    William~E.~Byrd, Usamichael~Ballantyne, Usagregory~Rosenblatt,
    Matthew~Might~// Relational Programming Workshop. \BibDash
  \newblock 2017.

  \bibitem{vanhoof2004binding}
  \selectlanguageifdefined{english}
  \BibEmph{Vanhoof~Wim, Bruynooghe~Maurice, Leuschel~Michael}. Binding-time
    analysis for Mercury~// Program Development in Computational Logic. \BibDash
  \newblock Springer, 2004. \BibDash
  \newblock P.~189--232.

  \bibitem{Varju2012UCL}
  \selectlanguageifdefined{english}
  \BibEmph{Varju~Zoltan, Littauer~Richard, Erins~Peteris}. Using Clojure in
    Linguistic Computing. \BibDash
  \newblock 2012. \BibDash 02.

  \bibitem{Wadler1985HRF}
  \selectlanguageifdefined{english}
  \BibEmph{Wadler~Philip}. How to Replace Failure by a List of Successes~// Proc.
    of a Conference on Functional Programming Languages and Computer
    Architecture. \BibDash
  \newblock Springer-Verlag, 1985. \BibDash
  \newblock P.~113–128.

  \bibitem{Near2008TAP}
  \selectlanguageifdefined{english}
  alphaleanTAP: A Declarative Theorem Prover for First-Order Classical Logic~/
    Joseph~Near, , William~E.~Byrd, Daniel~Friedman. \BibDash
  \newblock 2008. \BibDash Dec. \BibDash
  \newblock P.~238--252.

  \bibitem{Schreye1994TLP}
  \selectlanguageifdefined{english}
  \BibEmph{de~Schreye~Danny, Decorte~Stefaan}. Termination of logic programs: the
    never-ending story~// \BibEmph{The Journal of Logic Programming}. \BibDash
  \newblock 1994. \BibDash
  \newblock Vol. 19-20. \BibDash
  \newblock P.~199 -- 260.

  \bibitem{Hudak2007history}
  \selectlanguageifdefined{english}
  A history of Haskell: Being lazy with class~/ Paul~Hudak, John~Hughes,
    Simon~Peyton~Jones, Philip~Wadler~// In Proceedings of the 3rd ACM SIGPLAN
    Conference on History of Programming Languages (HOPL-III. \BibDash
  \newblock ACM Press, 2007. \BibDash
  \newblock P.~1--55.

  \end{thebibliography}


% \bibliographystyle{ugost2008ls}
% \bibliography{Artemeva/contents/bibfile}

