\begin{thebibliography}{10}
	\def\selectlanguageifdefined#1{
		\expandafter\ifx\csname date#1\endcsname\relax
		\else\selectlanguage{#1}\fi}
	\providecommand*{\href}[2]{{\small #2}}
	\providecommand*{\url}[1]{{\small #1}}
	\providecommand*{\BibUrl}[1]{\url{#1}}
	\providecommand{\BibAnnote}[1]{}
	\providecommand*{\BibEmph}[1]{#1}
	\ProvideTextCommandDefault{\cyrdash}{\iflanguage{russian}{\hbox
			to.8em{--\hss--}}{\textemdash}}
	\providecommand*{\BibDash}{\ifdim\lastskip>0pt\unskip\nobreak\hskip.2em plus
		0.1em\fi
		\cyrdash\hskip.2em plus 0.1em\ignorespaces}
	\renewcommand{\newblock}{\ignorespaces}
	
	\bibitem{ANTLRa}
	\selectlanguageifdefined{english}
	ANTLR Project website. \BibDash
	\newblock \url{http://www.antlr.org/}.
	
	\bibitem{afroozeh2015faster}
	\selectlanguageifdefined{english}
	\BibEmph{Afroozeh~Ali, Izmaylova~Anastasia}. Faster, Practical {GLL} Parsing~//
	International Conference on Compiler Construction~/ Springer. \BibDash
	\newblock 2015. \BibDash
	\newblock P.~89--108.
	
	\bibitem{aho1974design}
	\selectlanguageifdefined{english}
	\BibEmph{Aho~Alfred~V, Hopcroft~John~E}. The design and analysis of computer
	algorithms. \BibDash
	\newblock Pearson Education India, 1974.
	
	\bibitem{AttributedELL}
	\selectlanguageifdefined{english}
	\BibEmph{Alblas~Henk, Schaap-Kruseman~Joos}. An attributed {ELL} (1)-parser
	generator~// International Workshop on Compiler Construction~/ Springer.
	\BibDash
	\newblock 1990. \BibDash
	\newblock P.~208--209.
	
	\bibitem{Bison}
	\selectlanguageifdefined{english}
	Bison Project website. \BibDash
	\newblock \url{https://www.gnu.org/software/bison/}.
	
	\bibitem{Breveglieri2014}
	\selectlanguageifdefined{english}
	\BibEmph{Breveglieri~Luca, Crespi~Reghizzi~Stefano, Morzenti~Angelo}.
	\href{http://dx.doi.org/10.1007/978-3-319-04921-2_18}{Shift-Reduce Parsers
		for Transition Networks}~// Language and Automata Theory and Applications:
	8th International Conference, LATA 2014, Madrid, Spain, March 10-14, 2014.
	Proceedings~/ Ed.\ by\ Adrian-Horia~Dediu, Carlos~Mart{\'i}n-Vide,
	Jos{\'e}-Luis~Sierra-Rodr{\'i}guez, Bianca~Truthe. \BibDash
	\newblock Cham~: Springer International Publishing, 2014. \BibDash
	\newblock P.~222--235. \BibDash
	\newblock
	ISBN:~\href{http://isbndb.com/search-all.html?kw=978-3-319-04921-2}{978-3-319-04921-2}.
	
	\bibitem{ELRR}
	\selectlanguageifdefined{english}
	\BibEmph{Breveglieri~Luca, Reghizzi~Stefano~Crespi, Morzenti~Angelo}.
	Shift-reduce parsers for transition networks~// International Conference on
	Language and Automata Theory and Applications~/ Springer. \BibDash
	\newblock 2014. \BibDash
	\newblock P.~222--235.
	
	\bibitem{PredictiveECFG}
	\selectlanguageifdefined{english}
	\BibEmph{Br{\"u}ggemann-Klein~Anne, Wood~Derick}. On predictive parsing and
	extended context-free grammars~// International Conference on Implementation
	and Application of Automata~/ Springer. \BibDash
	\newblock 2002. \BibDash
	\newblock P.~239--247.
	
	\bibitem{ECFGparsing}
	\selectlanguageifdefined{english}
	\BibEmph{Bruggemann-Klein~Anne, Wood~Derick}. The parsing of extended
	context-free grammars. \BibDash
	\newblock 2002.
	
	\bibitem{ELLParser}
	\selectlanguageifdefined{english}
	\BibEmph{Heckmann~Reinhold}. An efficient {ELL} (1)-parser generator~//
	\BibEmph{Acta Informatica}. \BibDash
	\newblock 1986. \BibDash
	\newblock Vol.~23, no.~2. \BibDash
	\newblock P.~127--148.
	
	\bibitem{ELL}
	\selectlanguageifdefined{english}
	\BibEmph{Heilbrunner~Stephan}. On the definition of {ELR} (k) and {ELL} (k)
	grammars~// \BibEmph{Acta Informatica}. \BibDash
	\newblock 1979. \BibDash
	\newblock Vol.~11, no.~2. \BibDash
	\newblock P.~169--176.
	
	\bibitem{ECFG}
	\selectlanguageifdefined{english}
	\BibEmph{Hemerik~Kees}. Towards a Taxonomy for {ECFG} and {RRPG} Parsing~//
	International Conference on Language and Automata Theory and Applications~/
	Springer. \BibDash
	\newblock 2009. \BibDash
	\newblock P.~410--421.
	
	\bibitem{hopcroft1971n}
	\selectlanguageifdefined{english}
	\BibEmph{Hopcroft~John~E.}. An n log n algorithm for minimizing states in a finite automaton~/ Stanford University~//
	\newblock 1971.
	
	\bibitem{lee1997characterization}
	\selectlanguageifdefined{english}
	\BibEmph{Lee~Gyung-Ok, Kim~Do-Hyung}. Characterization of extended LR (k)
	grammars~// \BibEmph{Information processing letters}. \BibDash
	\newblock 1997. \BibDash
	\newblock Vol.~64, no.~2. \BibDash
	\newblock P.~75--82.
	
	\bibitem{ELALR}
	\selectlanguageifdefined{english}
	\BibEmph{Morimoto~Shin-ichi, Sassa~Masataka}. Yet another generation of {LALR}
	parsers for regular right part grammars~// \BibEmph{Acta informatica}.
	\BibDash
	\newblock 2001. \BibDash
	\newblock Vol.~37, no.~9. \BibDash
	\newblock P.~671--697.
	
	\bibitem{Infernal}
	\selectlanguageifdefined{english}
	\BibEmph{Nawrocki~Eric~P, Eddy~Sean~R}. Infernal 1.1: 100-fold faster RNA
	homology searches~// \BibEmph{Bioinformatics}. \BibDash
	\newblock 2013. \BibDash
	\newblock Vol.~29, no.~22. \BibDash
	\newblock P.~2933--2935.
	
	\bibitem{ELRParsing}
	\selectlanguageifdefined{english}
	\BibEmph{Purdom~Jr~Paul~Walton, Brown~Cynthia~A}. Parsing extended {LR} (k)
	grammars~// \BibEmph{Acta Informatica}. \BibDash
	\newblock 1981. \BibDash
	\newblock Vol.~15, no.~2. \BibDash
	\newblock P.~115--127.
	
	\bibitem{Anderson2013a}
	\selectlanguageifdefined{english}
	\BibEmph{James~WJ~Anderson, {\'A}d{\'a}m~Nov{\'a}k, Zsuzsanna~S{\"u}k{\"o}sd et~al.}. 
	Quantifying variances in comparative RNA secondary structure prediction~//
	\href{http://dx.doi.org/10.1186/1471-2105-14-149}{\BibEmph{BMC
			Bioinformatics}}. \BibDash
	\newblock 2013. \BibDash
	\newblock Vol.~14, no.~1. \BibDash
	\newblock P.~149.
	
	\bibitem{ragozina}
	\selectlanguageifdefined{english}
	\BibEmph{Ragozina~Anastasiya}. {GLL}-based relaxed parsing of dynamically
	generated code~: Master’s Thesis~; SpBU. \BibDash
	\newblock 2016.
	
	\bibitem{reago}
	\selectlanguageifdefined{english}
	\BibEmph{Cheng~Yuan, Jikai~Lei,
	James~Cole, Yanni~Sun}.
	Reconstructing 16S rRNA genes in metagenomic data~// \BibEmph{Bioinformatics}. \BibDash
	\newblock 2015. \BibDash
	\newblock Vol.~31, no.~12. \BibDash
	\newblock P.~i35--i43.
	
	\bibitem{SPPFa}
	\selectlanguageifdefined{english}
	\BibEmph{Rekers~Joan~Gerard}. Parser generation for interactive environments~:
	Ph.\,D. thesis~; Universiteit van Amsterdam. \BibDash
	\newblock 1992.
	
	\bibitem{scott2010gll}
	\selectlanguageifdefined{english}
	\BibEmph{Scott~Elizabeth, Johnstone~Adrian}. {GLL} parsing~//
	\BibEmph{Electronic Notes in Theoretical Computer Science}. \BibDash
	\newblock 2010. \BibDash
	\newblock Vol. 253, no.~7. \BibDash
	\newblock P.~177--189.
	
	\bibitem{scott2013gll}
	\selectlanguageifdefined{english}
	\BibEmph{Scott~Elizabeth, Johnstone~Adrian}. {GLL} parse-tree generation~//
	\BibEmph{Science of Computer Programming}. \BibDash
	\newblock 2013. \BibDash
	\newblock Vol.~78, no.~10. \BibDash
	\newblock P.~1828--1844.
	
	\bibitem{scott2016structuring}
	\selectlanguageifdefined{english}
	\BibEmph{Scott~Elizabeth, Johnstone~Adrian}. Structuring the {GLL} parsing
	algorithm for performance~// \BibEmph{Science of Computer Programming}.
	\BibDash
	\newblock 2016. \BibDash
	\newblock Vol. 125. \BibDash
	\newblock P.~1--22.
	
	\bibitem{brnglr}
	\selectlanguageifdefined{english}
	\BibEmph{Scott~Elizabeth, Johnstone~Adrian, Economopoulos~Rob}. {BRNGLR}: a
	cubic Tomita-style {GLR} parsing algorithm~// \BibEmph{Acta informatica}.
	\BibDash
	\newblock 2007. \BibDash
	\newblock Vol.~44, no.~6. \BibDash
	\newblock P.~427--461.
	
	\bibitem{tellier2006learning}
	\selectlanguageifdefined{english}
	\BibEmph{Tellier~Isabelle}. Learning recursive automata from positive
	examples~// \BibEmph{Revue des Sciences et Technologies de
		l'Information-S{\'e}rie RIA: Revue d'Intelligence Artificielle}. \BibDash
	\newblock 2006. \BibDash
	\newblock Vol.~20, no.~6. \BibDash
	\newblock P.~775--804.
	
	\bibitem{Thompson:1968:PTR:363347.363387}
	\selectlanguageifdefined{english}
	\BibEmph{Thompson~Ken}. Programming Techniques: Regular Expression Search
	Algorithm~// \href{http://dx.doi.org/10.1145/363347.363387}{\BibEmph{Commun.
			ACM}}. \BibDash
	\newblock 1968. \BibDash Jun. \BibDash
	\newblock Vol.~11, no.~6. \BibDash
	\newblock P.~419--422.
	
	\bibitem{hmmer}
	\selectlanguageifdefined{english}
	\BibEmph{Wheeler~Travis~J, Eddy~Sean~R}. nhmmer: DNA homology search with
	profile HMMs~// \BibEmph{Bioinformatics}. \BibDash
	\newblock 2013. \BibDash
	\newblock P.~btt403.
	
	\bibitem{EBNFISO}
	\selectlanguageifdefined{english}
	\BibEmph{Wirth~Niklaus}. Extended Backus-Naur Form ({EBNF})~//
	\BibEmph{ISO/IEC}. \BibDash
	\newblock 1996. \BibDash
	\newblock Vol. 14977. \BibDash
	\newblock P.~2996.
	
	\bibitem{xander}
	\selectlanguageifdefined{english}
	\BibEmph{Qiong~Wang, Jordan~A.~Fish, Mariah~Gilman et~al.}. Xander: employing a novel method for efficient gene-targeted metagenomic
	assembly~//
	\href{http://dx.doi.org/10.1186/s40168-015-0093-6}{\BibEmph{Microbiome}}.
	\BibDash
	\newblock 2015. \BibDash
	\newblock Vol.~3, no.~1. \BibDash
	\newblock P.~32.
	
	\bibitem{YaccConstructor}
	\selectlanguageifdefined{russian}
	YaccConstructor [Электронный ресурс]. \BibDash
	\newblock {Режим доступа}:
	\BibUrl{https://github.com/YaccConstructor/YaccConstructor} ({дата обращения}:
	01.12.2017).
	
\end{thebibliography}
