\begin{thebibliography}{10}
  \def\selectlanguageifdefined#1{
  \expandafter\ifx\csname date#1\endcsname\relax
  \else\selectlanguage{#1}\fi}
  \providecommand*{\href}[2]{{\small #2}}
  \providecommand*{\url}[1]{{\small #1}}
  \providecommand*{\BibUrl}[1]{\url{#1}}
  \providecommand{\BibAnnote}[1]{}
  \providecommand*{\BibEmph}[1]{#1}
  \ProvideTextCommandDefault{\cyrdash}{\iflanguage{russian}{\hbox
    to.8em{--\hss--}}{\textemdash}}
  \providecommand*{\BibDash}{\ifdim\lastskip>0pt\unskip\nobreak\hskip.2em plus
    0.1em\fi
  \cyrdash\hskip.2em plus 0.1em\ignorespaces}
  \renewcommand{\newblock}{\ignorespaces}

  \bibitem{interleaving}
  \selectlanguageifdefined{english}
  Backtracking, Interleaving, and Terminating Monad Transformers: (Functional
    Pearl)~/ Oleg~Kiselyov, Chung-chieh~Shan, Daniel~P.~Friedman, Amr~Sabry~//
    \href{http://dx.doi.org/10.1145/1090189.1086390}{\BibEmph{SIGPLAN Not.}}
    \BibDash
  \newblock 2005. \BibDash Sep. \BibDash
  \newblock Vol.~40, no.~9. \BibDash
  \newblock P.~192–203. \BibDash
  \newblock Access mode: \BibUrl{https://doi.org/10.1145/1090189.1086390}.

  \bibitem{scHaskell}
  \selectlanguageifdefined{english}
  \BibEmph{Bolingbroke~Maximilian, Peyton~Jones~Simon}. Supercompilation by
    Evaluation~//
    \href{http://dx.doi.org/10.1145/2088456.1863540}{\BibEmph{SIGPLAN Not.}}
    \BibDash
  \newblock 2010. \BibDash Sep. \BibDash
  \newblock Vol.~45, no.~11. \BibDash
  \newblock P.~135–146. \BibDash
  \newblock Access mode: \BibUrl{https://doi.org/10.1145/2088456.1863540}.

  \bibitem{prologInt}
  \selectlanguageifdefined{english}
  \BibEmph{Bratko~Ivan}. Prolog programming for artificial intelligence (4th
    ed.). \BibDash
  \newblock Harlow, England ; New York: Addison Wesley.

  \bibitem{byrdMK}
  \selectlanguageifdefined{english}
  \BibEmph{Byrd~William}. Relational Programming in miniKanren: Techniques,
    Applications, and Implementations. \BibDash
  \newblock 2009. \BibDash 09. \BibDash
  \newblock P.~297.

  \bibitem{cpd}
  \selectlanguageifdefined{english}
  Conjunctive partial deduction: Foundations, control, algorithms, and
    experiments~/ Danny~De~Schreye, Robert~Gl{\"u}ck, Jesper~J{\o}rgensen
    et~al.~// \BibEmph{The Journal of Logic Programming}. \BibDash
  \newblock 1999. \BibDash
  \newblock Vol.~41, no. 2-3. \BibDash
  \newblock P.~231--277.

  \bibitem{apropos}
  \selectlanguageifdefined{english}
  \BibEmph{Diehl~Stephan}. A Prolog Positive Supercompiler. \BibDash
  \newblock 1997.

  \bibitem{reasonedSchemer}
  \selectlanguageifdefined{english}
  \BibEmph{Friedman~Daniel~P., Byrd~William~E., Kiselyov~Oleg}. The Reasoned
    Schemer. \BibDash
  \newblock The MIT Press, 2005. \BibDash
  \newblock
    ISBN:~\href{http://isbndb.com/search-all.html?kw=0262562146}{0262562146}.

  \bibitem{futamura}
  \selectlanguageifdefined{english}
  \BibEmph{Futamura~Yoshihiko}. Partial Evaluation of Computation Process - An
    Approach to a Compiler-Compiler~// \BibEmph{Systems, Computers, Controls}.
    \BibDash
  \newblock 1999. \BibDash
  \newblock Vol.~2. \BibDash
  \newblock P.~45--50.

  \bibitem{pdAndDriving}
  \selectlanguageifdefined{english}
  \BibEmph{Glück~Robert, Sørensen~Morten~Heine}. Partial Deduction and Driving
    are Equivalent~// Lecture Notes in Computer Science. \BibDash
  \newblock Springer, Berlin, Heidelberg, 1994.

  \bibitem{currySearch}
  \selectlanguageifdefined{english}
  \BibEmph{Hanus~M., Peem{\"o}ller~B., Reck~F.} Search Strategies for Functional
    Logic Programming~// Proc. of the 5th Working Conference on Programming
    Languages (ATPS'12). \BibDash
  \newblock Springer LNI 199, 2012. \BibDash
  \newblock P.~61--74.

  \bibitem{curry}
  \selectlanguageifdefined{english}
  \BibEmph{Hanus~(ed.)~M.} Curry: An Integrated Functional Logic Language (Vers.\
    0.9.0). \BibDash
  \newblock Available at \url{http://www.curry-language.org}. \BibDash
  \newblock 2016.

  \bibitem{uKanren}
  \selectlanguageifdefined{english}
  \BibEmph{Hemann~Jason, Friedman~Daniel~P.} $\mu$Kanren: A Minimal Functional
    Core for Relational Programming~// Proceedings of the 2013 Annual Workshop on
    Scheme and Functional Programming. \BibDash
  \newblock 2013.

  \bibitem{prologTheorem}
  \selectlanguageifdefined{english}
  \BibEmph{Hsiang~Jieh, Srivas~Mandayam}. Automatic inductive theorem proving
    using prolog~//
    \href{http://dx.doi.org/https://doi.org/10.1016/0304-3975(87)90016-8}{\BibEmph{Theoretical
    Computer Science}}. \BibDash
  \newblock 1987. \BibDash
  \newblock Vol.~54, no.~1. \BibDash
  \newblock P.~3 -- 28. \BibDash
  \newblock Access mode:
    \BibUrl{http://www.sciencedirect.com/science/article/pii/0304397587900168}.

  \bibitem{zipper}
  \selectlanguageifdefined{english}
  \BibEmph{Huet~G\'{e}rard}. The Zipper~//
    \href{http://dx.doi.org/10.1017/S0956796897002864}{\BibEmph{J. Funct.
    Program.}} \BibDash
  \newblock 1997. \BibDash Sep. \BibDash
  \newblock Vol.~7, no.~5. \BibDash
  \newblock P.~549–554. \BibDash
  \newblock Access mode: \BibUrl{https://doi.org/10.1017/S0956796897002864}.

  \bibitem{jones}
  \selectlanguageifdefined{english}
  \BibEmph{Jones~Neil~D, Gomard~Carsten~K, Sestoft~Peter}. Partial evaluation and
    automatic program generation. \BibDash
  \newblock Peter Sestoft, 1993.

  \bibitem{prologPE}
  \selectlanguageifdefined{english}
  \BibEmph{Jørgensen~Jesper, Leuschel~Michael}. Efficiently generating efficient
    generating extensions in Prolog~// Partial Evaluation, International Seminar,
    LNCS 1110, pages 238–262, Schloß Dagstuhl. \BibDash
  \newblock Springer-Verlag, 1996. \BibDash
  \newblock P.~238--262.

  \bibitem{cpdPract}
  \selectlanguageifdefined{english}
  \BibEmph{Jørgensen~Jesper, Leuschel~Michael, Martens~Bern}. Conjunctive
    partial deduction in practice~// Proceedings of the International Workshop on
    Logic Program Synthesis and Transformation (LOPSTR'96), LNCS 1207. \BibDash
  \newblock Springer-Verlag, 1996. \BibDash
  \newblock P.~59--82.

  \bibitem{scJava}
  \selectlanguageifdefined{english}
  \BibEmph{Klimov~Andrei~V.} An Approach to Supercompilation for Object-oriented
    Languages: the Java Supercompiler Case Study. \BibDash
  \newblock 2008.

  \bibitem{simplesc}
  \selectlanguageifdefined{english}
  \BibEmph{Klyuchnikov~Ilya, Romanenko~Sergei}. SPSC: a Simple Supercompiler in
    Scala. \BibDash
  \newblock 2009.

  \bibitem{ocanren}
  \selectlanguageifdefined{english}
  \BibEmph{Kosarev~Dmitrii, Boulytchev~Dmitri}. Typed Embedding of a Relational
    Language in OCaml~//
    \href{http://dx.doi.org/10.4204/EPTCS.285.1}{\BibEmph{Electronic Proceedings
    in Theoretical Computer Science}}. \BibDash
  \newblock 2018. \BibDash 12. \BibDash
  \newblock Vol. 285. \BibDash
  \newblock P.~1--22.

  \bibitem{unifRev}
  \selectlanguageifdefined{english}
  \BibEmph{Lassez~Jean-Louis, Maher~Michael, Marriott~Kim}.
    \href{http://dx.doi.org/10.1007/3-540-19129-1_4}{Unification Revisited}.
    \BibDash
  \newblock 2006. \BibDash 01. \BibDash
  \newblock Vol.~306. \BibDash
  \newblock P.~67--113.

  \bibitem{unification}
  \selectlanguageifdefined{english}
  \BibEmph{Lassez~Jean-Louis, Maher~Michael, Marriott~Kim}.
    \href{http://dx.doi.org/10.1007/3-540-19129-1_4}{Unification Revisited}.
    \BibDash
  \newblock 2006. \BibDash 01. \BibDash
  \newblock Vol.~306. \BibDash
  \newblock P.~67--113.

  \bibitem{advanced}
  \selectlanguageifdefined{english}
  Advanced Techniques for Logic Program Specialisation~: Rep.~; Executor:
    Michael~Leuschel~: 1997.

  \bibitem{ecce}
  \selectlanguageifdefined{english}
  The ecce Partial Deduction System~: Rep.~/ In Proc. of the ILPS'97 Workshop on
    Tools and Environments for (Constraint) Logic Programming, U.P~; Executor:
    Michael~Leuschel~: 1997.

  \bibitem{homeo}
  \selectlanguageifdefined{english}
  \BibEmph{Leuschel~Michael}. Homeomorphic embedding for online termination of
    symbolic methods~// In The essence of computation, volume 2566 of LNCS.
    \BibDash
  \newblock Springer, 2002. \BibDash
  \newblock P.~379--403.

  \bibitem{controlPoly}
  \selectlanguageifdefined{english}
  \BibEmph{Leuschel~Michael, Martens~Bern, De~Schreye~Danny}. Controlling
    Generalization and Polyvariance in Partial Deduction of Normal Logic
    Programs~// \href{http://dx.doi.org/10.1145/271510.271525}{\BibEmph{ACM
    Trans. Program. Lang. Syst.}} \BibDash
  \newblock 1998. \BibDash Jan. \BibDash
  \newblock Vol.~20, no.~1. \BibDash
  \newblock P.~208–258. \BibDash
  \newblock Access mode: \BibUrl{https://doi.org/10.1145/271510.271525}.

  \bibitem{raf}
  \selectlanguageifdefined{english}
  \BibEmph{Leuschel~Michael, Soerensen~Morten~Heine}. Redundant Argument
    Filtering of Logic Programs. \BibDash
  \newblock Springer-Verlag, 1996. \BibDash
  \newblock P.~83--103.

  \bibitem{lozov}
  \selectlanguageifdefined{english}
  \BibEmph{Lozov~Petr, Verbitskaia~Ekaterina, Boulytchev~Dmitry}. Relational
    Interpreters for Search Problems~// Relational Programming Workshop. \BibDash
  \newblock 2019. \BibDash
  \newblock P.~43.

  \bibitem{trconv}
  \selectlanguageifdefined{english}
  \BibEmph{Lozov~P.~Vyatkin~A.~Boulytchev~D.} Typed Relational Conversion~//
    \BibEmph{Wang M., Owens S. (eds) Trends in Functional Programming. TFP 2017.
    Lecture Notes in Computer Science, vol 10788. Springer, Cham}. \BibDash
  \newblock 2018.

  \bibitem{relML}
  \selectlanguageifdefined{english}
  Introduction to relational programming~: Rep.~; Executor: Bruce~J.~MacLennan~:
    1981.

  \bibitem{prologExSys}
  \selectlanguageifdefined{english}
  \BibEmph{Merritt~Dennis}. Building Expert Systems in Prolog. \BibDash
  \newblock Spring-Verlag, 1989.

  \bibitem{medMK}
  \selectlanguageifdefined{english}
  \BibEmph{Might~Matthew}. \href{http://dx.doi.org/10.1145/3359061.3365208}{The
    Algorithm for Precision Medicine (Invited Talk)}~// Proceedings Companion of
    the 2019 ACM SIGPLAN International Conference on Systems, Programming,
    Languages, and Applications: Software for Humanity. \BibDash
  \newblock SPLASH Companion 2019. \BibDash
  \newblock New York, NY, USA~: Association for Computing Machinery, 2019.
    \BibDash
  \newblock P.~2. \BibDash
  \newblock Access mode: \BibUrl{https://doi.org/10.1145/3359061.3365208}.

  \bibitem{mkProver}
  \selectlanguageifdefined{english}
  \BibEmph{Near~Joseph, Byrd~William, Friedman~Daniel}.
    \href{http://dx.doi.org/10.1007/978-3-540-89982-2_26}{aleanTAP: A Declarative
    Theorem Prover for First-Order Classical Logic}. \BibDash
  \newblock Vol.~5366. \BibDash
  \newblock 2008. \BibDash 12. \BibDash
  \newblock P.~238--252.

  \bibitem{optimus}
  \selectlanguageifdefined{english}
  Optimus Prime: A new tool for interactive transformation and supercompilation
    of functional programs~: Rep.~/ The University of York, Department of
    Computer Science~; Executor: Jason~S.~Reich~: 2009.

  \bibitem{semanticMK}
  \selectlanguageifdefined{english}
  \BibEmph{Rozplokhas~Dmitry, Boulytchev~Dmitry}. Certified Semantics for
    miniKanren~// miniKanren and Relational Programming Workshop. \BibDash
  \newblock 2019.

  \bibitem{scPerf}
  \selectlanguageifdefined{english}
  \BibEmph{Secher~Jens~Peter, Sørensen~Morten~Heine}. On perfect
    supercompilation~// \BibEmph{Journal of Functional Programming}. \BibDash
  \newblock 1996. \BibDash
  \newblock Vol.~6. \BibDash
  \newblock P.~465--479.

  \bibitem{soerensen1996positive}
  \selectlanguageifdefined{english}
  \BibEmph{Soerensen~Morten~Heine, Gl{\"u}ck~Robert, Jones~Neil~D.} A positive
    supercompiler~// \BibEmph{Journal of functional programming}. \BibDash
  \newblock 1996. \BibDash
  \newblock Vol.~6, no.~6. \BibDash
  \newblock P.~811--838.

  \bibitem{mercury}
  \selectlanguageifdefined{english}
  \BibEmph{Somogyi~Zoltan, Henderson~Fergus~James, Conway~Thomas~Charles}. The
    implementation of Mercury, an efficient purely declarative logic programming
    language~// IN PROCEEDINGS OF THE AUSTRALIAN COMPUTER SCIENCE CONFERENCE.
    \BibDash
  \newblock 1995. \BibDash
  \newblock P.~499--512.

  \bibitem{scGen}
  \selectlanguageifdefined{english}
  \BibEmph{S{\o}rensen~Morten~Heine, Gl{\"u}ck~Robert}. An Algorithm of
    Generalization in Positive Supercompilation~// ILPS. \BibDash
  \newblock 1995.

  \bibitem{scPos}
  \selectlanguageifdefined{english}
  \BibEmph{S\o{}rensen~Morten~Heine, Gl\"{u}ck~Robert}. Introduction to
    Supercompilation~// Partial Evaluation - Practice and Theory, DIKU 1998
    International Summer School. \BibDash
  \newblock Berlin, Heidelberg~: Springer-Verlag, 1998. \BibDash
  \newblock P.~246–270.

  \bibitem{offlinePD}
  \selectlanguageifdefined{english}
  \href{http://dx.doi.org/10.1007/978-3-540-25951-0_11}{Specialising Interpreters
    Using Offline Partial Deduction}~/ Michael~Leuschel, Stephen-John~Craig,
    Maurice~Bruynooghe, Wim~Vanhoof. \BibDash
  \newblock Vol.~3049. \BibDash
  \newblock 2004. \BibDash 01. \BibDash
  \newblock P.~340--375.

  \bibitem{scompRevisited}
  \selectlanguageifdefined{english}
  \BibEmph{Sørensen~Morten~Heine}. Turchin's Supercompiler Revisited - An
    operational theory of positive information propagation. \BibDash
  \newblock 1996.

  \bibitem{tupling}
  \selectlanguageifdefined{english}
  Tupling Calculation Eliminates Multiple Data Traversals~/ Zhenjiang~Hu,
    Hideya~Iwasaki, Masato~Takeichi, Akihiko~Takano~//
    \href{http://dx.doi.org/10.1145/258948.258964}{\BibEmph{ACM SIGPLAN
    Notices}}. \BibDash
  \newblock 1997. \BibDash 12. \BibDash
  \newblock Vol.~32.

  \bibitem{turchinSC}
  \selectlanguageifdefined{english}
  \BibEmph{Turchin~Valentin~F.} The Concept of a Supercompiler~// \BibEmph{ACM
    Transactions on Programming Languages and Systems}. \BibDash
  \newblock 1986. \BibDash
  \newblock Vol.~8. \BibDash
  \newblock P.~292--325.

  \bibitem{unifiedMK}
  \selectlanguageifdefined{english}
  A Unified Approach to Solving Seven Programming Problems (Functional Pearl)~/
    William~E.~Byrd, Michael~Ballantyne, Gregory~Rosenblatt, Matthew~Might~//
    \href{http://dx.doi.org/10.1145/3110252}{\BibEmph{Proc. ACM Program. Lang.}}
    \BibDash
  \newblock 2017. \BibDash Aug. \BibDash
  \newblock Vol.~1, no. ICFP. \BibDash
  \newblock Access mode: \BibUrl{https://doi.org/10.1145/3110252}.

  \bibitem{mkLing}
  \selectlanguageifdefined{english}
  \BibEmph{Varju~Zoltan, Littauer~Richard, Erins~Peteris}. Using Clojure in
    Linguistic Computing. \BibDash
  \newblock 2012. \BibDash 02.

  \bibitem{deforest}
  \selectlanguageifdefined{english}
  \BibEmph{Wadler~Philip}. Deforestation: Transforming Programs to Eliminate
    Trees~// Proceedings of the 2nd European Symposium on Programming. \BibDash
  \newblock ESOP ’88. \BibDash
  \newblock Berlin, Heidelberg~: Springer-Verlag, 1988. \BibDash
  \newblock P.~344–358.

  \bibitem{mkConstr}
  \selectlanguageifdefined{english}
  cKanren miniKanren with Constraints~/ Claire~E.~Alvis, Jeremiah~J.~Willcock,
    Kyle~M.~Carter et~al.~// In Proceedings of the 2011 Workshop on Scheme and
    Functional Programming (Scheme '11), Portland, OR. \BibDash
  \newblock 2011.

  \bibitem{scmini}
  \selectlanguageifdefined{russian}
  \BibEmph{Ключников~Илья.} Суперкомпиляция: идеи
    и методы~// \BibEmph{Практика функционального
    программирования, №7.} \BibDash
  \newblock 2011.

  \bibitem{logicMJ}
  \selectlanguageifdefined{russian}
  \BibEmph{Малпас~Дж.} Реляционный язык Пролог и
    его применение. \BibDash
  \newblock M.: Наука, 1990.

  \end{thebibliography}
