\begin{thebibliography}{10}
\def\selectlanguageifdefined#1{
\expandafter\ifx\csname date#1\endcsname\relax
\else\selectlanguage{#1}\fi}
\providecommand*{\href}[2]{{\small #2}}
\providecommand*{\url}[1]{{\small #1}}
\providecommand*{\BibUrl}[1]{\url{#1}}
\providecommand{\BibAnnote}[1]{}
\providecommand*{\BibEmph}[1]{#1}
\ProvideTextCommandDefault{\cyrdash}{\iflanguage{russian}{\hbox
  to.8em{--\hss--}}{\textemdash}}
\providecommand*{\BibDash}{\ifdim\lastskip>0pt\unskip\nobreak\hskip.2em plus
  0.1em\fi
\cyrdash\hskip.2em plus 0.1em\ignorespaces}
\renewcommand{\newblock}{\ignorespaces}

\bibitem{augustsson1985compiling}
\selectlanguageifdefined{russian}
\BibEmph{Augustsson~Lennart}. Compiling pattern matching~// Functional
  Programming Languages and Computer Architecture~/ Под ред.\
  Jean-Pierre~Jouannaud. \BibDash
\newblock Berlin, Heidelberg~: Springer Berlin Heidelberg, 1985. \BibDash
\newblock {С.}~368--381.

\bibitem{myrfc}
\selectlanguageifdefined{russian}
\BibEmph{Bashkirov~Alexander}. Active patterns for OCaml. \BibDash
\newblock 2020. \BibDash
\newblock {Режим доступа}:
  \BibUrl{https://github.com/ocaml/RFCs/pull/12} ({дата
  обращения}: 01.06.2020).

\bibitem{myrepo}
\selectlanguageifdefined{russian}
\BibEmph{Bashkirov~Alexander}. Active patterns for OCaml implementation
  repository. \BibDash
\newblock 2020. \BibDash
\newblock {Режим доступа}:
  \BibUrl{https://github.com/bash-spbu/ocaml/tree/active_patterns_docker_image}
  ({дата обращения}: 01.06.2020).

\bibitem{java2019proposal}
\selectlanguageifdefined{russian}
\BibEmph{Brian~Goetz}. Data Classes and Sealed Types for Java. \BibDash
\newblock 2019. \BibDash
\newblock {Режим доступа}:
  \BibUrl{https://cr.openjdk.java.net/~briangoetz/amber/datum.html} ({дата
  обращения}: 20.05.2020).

\bibitem{emir2007objects}
\selectlanguageifdefined{russian}
\BibEmph{Emir~Burak, Odersky~Martin, Williams~John}. Matching Objects with
  Patterns~// Proceedings of the 21st European Conference on Object-Oriented
  Programming. \BibDash
\newblock ECOOP'07. \BibDash
\newblock Berlin, Heidelberg~: Springer-Verlag, 2007. \BibDash
\newblock {С.}~273--298. \BibDash
\newblock {Режим доступа}:
  \BibUrl{http://dl.acm.org/citation.cfm?id=2394758.2394779}.

\bibitem{erwig2000pattern}
\selectlanguageifdefined{russian}
\BibEmph{Erwig~Martin, Peyton~Jones~Simon}. Pattern Guards and Transformational
  Patterns~// Haskell Workshop 2000. \BibDash
\newblock 2000. \BibDash September. \BibDash
\newblock {Режим доступа}:
  \BibUrl{https://www.microsoft.com/en-us/research/publication/pattern-guards-and-transformational-patterns/}.

\bibitem{viewshaskell}
\selectlanguageifdefined{russian}
\BibEmph{GHC~Wiki}. Haskell view patterns. \BibDash
\newblock {Режим доступа}:
  \BibUrl{https://gitlab.haskell.org/ghc/ghc/wikis/view-patterns} ({дата
  обращения}: 20.05.2020).

\bibitem{unexpresiveness_example}
\selectlanguageifdefined{russian}
\BibEmph{IntelliJ~Scala}. Демонстрация
  невыразительности сопоставления на
  примере конвертера из языка Scala в UAST. \BibDash
\newblock {Режим доступа}:
  \BibUrl{https://github.com/JetBrains/intellij-scala/blob/878ef964b1bb9dc535ed0bb42ad7ea0731427065/scala/uast/src/org/jetbrains/plugins/scala/lang/psi/uast/converter/Scala2UastConverter.scala\#L366}
  ({дата обращения}: 20.05.2020).

\bibitem{kotlin2019when_expression}
\selectlanguageifdefined{russian}
\BibEmph{Kotlin~Language~Documentation}. Control Flow: When Expression.
  \BibDash
\newblock 2019. \BibDash
\newblock {Режим доступа}:
  \BibUrl{https://kotlinlang.org/docs/reference/control-flow.html\#when-expression}
  ({дата обращения}: 20.05.2020).

\bibitem{fessant2001optimizing}
\selectlanguageifdefined{russian}
\BibEmph{Le~Fessant~Fabrice, Maranget~Luc}. Optimizing Pattern Matching~//
  \href{http://dx.doi.org/10.1145/507635.507641}{\BibEmph{ACM SIGPLAN
  Notices}}. \BibDash
\newblock 2001. \BibDash 08. \BibDash
\newblock Т.~36.

\bibitem{maranget2007warnings}
\selectlanguageifdefined{russian}
\BibEmph{Maranget~Luc}. Warnings for pattern matching~//
  \href{http://dx.doi.org/10.1017/S0956796807006223}{\BibEmph{Journal of
  Functional Programming}}. \BibDash
\newblock 2007. \BibDash 05. \BibDash
\newblock Т.~17. \BibDash
\newblock {С.}~387--421.

\bibitem{maranget2008decisiontrees}
\selectlanguageifdefined{russian}
\BibEmph{Maranget~Luc}.
  \href{http://dx.doi.org/10.1145/1411304.1411311}{Compiling Pattern Matching
  to Good Decision Trees}~// Proceedings of the 2008 ACM SIGPLAN Workshop on
  ML. \BibDash
\newblock ML '08. \BibDash
\newblock New York, NY, USA~: ACM, 2008. \BibDash
\newblock {С.}~35--46. \BibDash
\newblock {Режим доступа}:
  \BibUrl{http://doi.acm.org/10.1145/1411304.1411311}.

\bibitem{csharp2019pattern_matching}
\selectlanguageifdefined{russian}
\BibEmph{Microsoft~Docs}. C\# Pattern Matching. \BibDash
\newblock 2019. \BibDash
\newblock {Режим доступа}:
  \BibUrl{https://docs.microsoft.com/en-us/dotnet/csharp/pattern-matching}
  ({дата обращения}: 20.05.2020).

\bibitem{milner1997definition}
\selectlanguageifdefined{russian}
\BibEmph{Milner~Robin, Tofte~Mads, Macqueen~David}. The Definition of Standard
  ML. \BibDash
\newblock Cambridge, MA, USA~: MIT Press, 1997. \BibDash
\newblock
  ISBN:~\href{http://isbndb.com/search-all.html?kw=0262631814}{0262631814}.

\bibitem{ocaml_iflet}
\selectlanguageifdefined{russian}
\BibEmph{OCaml~Community}. if-let for OCaml. \BibDash
\newblock {Режим доступа}:
  \BibUrl{https://github.com/ocaml/ocaml/pull/194} ({дата
  обращения}: 20.05.2020).

\bibitem{discuss}
\selectlanguageifdefined{russian}
\BibEmph{OCaml~Discuss}. Musings on extended pattern-matching syntaxes.
  \BibDash
\newblock 2019. \BibDash
\newblock {Режим доступа}:
  \BibUrl{https://discuss.ocaml.org/t/musings-on-extended-pattern-matching-syntaxes/3600}
  ({дата обращения}: 20.05.2020).

\bibitem{okasaki98views}
\selectlanguageifdefined{russian}
\BibEmph{Okasaki~Chris}. Views for Standard ML~// In SIGPLAN Workshop on ML.
  \BibDash
\newblock 1998. \BibDash
\newblock {С.}~14--23.

\bibitem{okmij_typechecker}
\selectlanguageifdefined{russian}
\BibEmph{Oleg~Kiselyov}. How OCaml type checker works -- or what polymorphism
  and garbage collection have in common. \BibDash
\newblock {Режим доступа}:
  \BibUrl{http://okmij.org/ftp/ML/generalization.html} ({дата
  обращения}: 20.05.2020).

\bibitem{pickering2016pattern}
\selectlanguageifdefined{russian}
Pattern Synonyms~/ Matthew~Pickering, Gergo~Érdi, Simon~Peyton~Jones,
  Richard~A.~Eisenberg~// Haskell'16. \BibDash
\newblock 2016. \BibDash September. \BibDash
\newblock {Режим доступа}:
  \BibUrl{https://www.microsoft.com/en-us/research/publication/pattern-synonyms/}.

\bibitem{peytonjones2020lower}
\selectlanguageifdefined{russian}
\BibEmph{Peyton~Jones~Simon, Graf~Sebastian, Scott~Ryan}. Lower your guards: a
  compositional pattern-match coverage checker. \BibDash
\newblock 2020. \BibDash March. \BibDash
\newblock In submission. {Режим доступа}:
  \BibUrl{https://www.microsoft.com/en-us/research/publication/lower-your-guards-a-compositional-pattern-match-coverage-checker/}.

\bibitem{rust_reference}
\selectlanguageifdefined{russian}
{The Rust reference}~: Intern report~/ {Inria}~; {исполн.}:
  Community~Rust~: 2020. \BibDash
\newblock {Режим доступа}:
  \BibUrl{https://doc.rust-lang.org/reference/index.html}.

\bibitem{scott2000whendo}
\selectlanguageifdefined{russian}
\BibEmph{Scott~Kevin~D, Ramsey~Norman}. When Do Match-compilation Heuristics
  Matter?~// Technical Report CS-2000-13. \BibDash
\newblock 2000.

\bibitem{syme2007extensible}
\selectlanguageifdefined{russian}
\BibEmph{Syme~Don, Neverov~Gregory, Margetson~James}. Extensible pattern
  matching via a lightweight language extension~// Proceedings of the 12th ACM
  SIGPLAN international conference on Functional programming. \BibDash
\newblock Association for Computing Machinery, Inc., 2007. \BibDash October.
  \BibDash
\newblock {Режим доступа}:
  \BibUrl{https://www.microsoft.com/en-us/research/publication/extensible-pattern-matching-via-a-lightweight-language-extension/}.

\bibitem{leroy2019manual}
\selectlanguageifdefined{russian}
{The OCaml system release 4.09: Documentation and user's manual}~: Intern
  report~/ {Inria}~; {исполн.}: Xavier~Leroy, Damien~Doligez,
  Alain~Frisch и~др.~: 2019. \BibDash Сент. \BibDash
\newblock {С.}~1--789. {Режим доступа}:
  \BibUrl{https://hal.inria.fr/hal-00930213}.

\bibitem{tullsen2000firstclass}
\selectlanguageifdefined{russian}
\BibEmph{Tullsen~Mark}. First Class Patterns~// In 2nd International Workshop
  on Practial Aspects of Declarative Languages, volume 1753 of LNCS. \BibDash
\newblock Springer-Verlag, 2000. \BibDash
\newblock {С.}~1--15.

\bibitem{wadler1987views}
\selectlanguageifdefined{russian}
\BibEmph{Wadler~P.} \href{http://dx.doi.org/10.1145/41625.41653}{Views: A Way
  for Pattern Matching to Cohabit with Data Abstraction}~// Proceedings of the
  14th ACM SIGACT-SIGPLAN Symposium on Principles of Programming Languages.
  \BibDash
\newblock POPL '87. \BibDash
\newblock New York, NY, USA~: ACM, 1987. \BibDash
\newblock {С.}~307--313. \BibDash
\newblock {Режим доступа}:
  \BibUrl{http://doi.acm.org/10.1145/41625.41653}.

\end{thebibliography}
