\begin{thebibliography}{10}
\def\selectlanguageifdefined#1{
\expandafter\ifx\csname date#1\endcsname\relax
\else\selectlanguage{#1}\fi}
\providecommand*{\href}[2]{{\small #2}}
\providecommand*{\url}[1]{{\small #1}}
\providecommand*{\BibUrl}[1]{\url{#1}}
\providecommand{\BibAnnote}[1]{}
\providecommand*{\BibEmph}[1]{#1}
\ProvideTextCommandDefault{\cyrdash}{\iflanguage{russian}{\hbox
  to.8em{--\hss--}}{\textemdash}}
\providecommand*{\BibDash}{\ifdim\lastskip>0pt\unskip\nobreak\hskip.2em plus
  0.1em\fi
\cyrdash\hskip.2em plus 0.1em\ignorespaces}
\renewcommand{\newblock}{\ignorespaces}

\bibitem{davies2015analysis}
\selectlanguageifdefined{english}
Analysis of 5’gene regions reveals extraordinary conservation of novel
  non-coding sequences in a wide range of animals~/ Nathaniel~J~Davies,
  Peter~Krusche, Eran~Tauber, Sascha~Ott~// \BibEmph{BMC evolutionary biology}.
  \BibDash
\newblock 2015. \BibDash
\newblock Vol.~15, no.~1. \BibDash
\newblock P.~227.

\bibitem{arslan2004dynamic}
\selectlanguageifdefined{english}
\BibEmph{Arslan~Abdullah~N, E{\u{g}}ecio{\u{g}}lu~{\"O}mer}. Dynamic
  programming based approximation algorithms for sequence alignment with
  constraints~// \BibEmph{INFORMS Journal on Computing}. \BibDash
\newblock 2004. \BibDash
\newblock Vol.~16, no.~4. \BibDash
\newblock P.~441--458.

\bibitem{blasi2018replicomment}
\selectlanguageifdefined{english}
\BibEmph{Blasi~Arianna, Gorla~Alessandra}. Replicomment: identifying clones in
  code comments~// Proceedings of the 26th Conference on Program Comprehension.
  \BibDash
\newblock 2018. \BibDash
\newblock P.~320--323.

\bibitem{juergens2010can}
\selectlanguageifdefined{english}
Can clone detection support quality assessments of requirements
  specifications?~/ Elmar~Juergens, Florian~Deissenboeck, Martin~Feilkas
  et~al.~// Proceedings of the 32nd ACM/IEEE International Conference on
  Software Engineering-Volume 2. \BibDash
\newblock 2010. \BibDash
\newblock P.~79--88.

\bibitem{chomal2014significance}
\selectlanguageifdefined{english}
\BibEmph{Chomal~Vikas~S, Saini~Jatinderkumar~R}. Significance of Software
  Documentation in Software Development Process~// \BibEmph{International
  Journal of Engineering Innovations and Research}. \BibDash
\newblock 2014. \BibDash
\newblock Vol.~3, no.~4. \BibDash
\newblock P.~410.

\bibitem{koznov2015clone}
\selectlanguageifdefined{english}
Clone detection in reuse of software technical documentation~/ Dmitrij~Koznov,
  Dmitry~Luciv, Hamid~Abdul~Basit et~al.~// International Andrei Ershov
  Memorial Conference on Perspectives of System Informatics~/ Springer.
  \BibDash
\newblock 2015. \BibDash
\newblock P.~170--185.

\bibitem{baxter2012conserved}
\selectlanguageifdefined{english}
Conserved noncoding sequences highlight shared components of regulatory
  networks in dicotyledonous plants~/ Laura~Baxter, Aleksey~Jironkin,
  Richard~Hickman et~al.~// \BibEmph{The Plant Cell}. \BibDash
\newblock 2012. \BibDash
\newblock Vol.~24, no.~10. \BibDash
\newblock P.~3949--3965.

\bibitem{luciv2018detecting}
\selectlanguageifdefined{english}
Detecting near duplicates in software documentation~/ DV~Luciv, DV~Koznov,
  George~A~Chernishev et~al.~// \BibEmph{Programming and Computer Software}.
  \BibDash
\newblock 2018. \BibDash
\newblock Vol.~44, no.~5. \BibDash
\newblock P.~335--343.

\bibitem{oumaziz2017documentation}
\selectlanguageifdefined{english}
Documentation reuse: Hot or not? An empirical study~/ Mohamed~A~Oumaziz,
  Alan~Charpentier, Jean-R{\'e}my~Falleri, Xavier~Blanc~// International
  Conference on Software Reuse~/ Springer. \BibDash
\newblock 2017. \BibDash
\newblock P.~12--27.

\bibitem{dongen2000cluster}
\selectlanguageifdefined{english}
\BibEmph{Dongen~Stijn}. A cluster algorithm for graphs. \BibDash
\newblock 2000.

\bibitem{luciv2018duplicate}
\selectlanguageifdefined{english}
Duplicate finder toolkit~/ Dmitry~Luciv, Dmitrij~Koznov, George~Chernishev
  et~al.~// Proceedings of the 40th International Conference on Software
  Engineering: Companion Proceeedings. \BibDash
\newblock 2018. \BibDash
\newblock P.~171--172.

\bibitem{picot2010evolutionary}
\selectlanguageifdefined{english}
Evolutionary analysis of regulatory sequences (EARS) in plants~/ Emma~Picot,
  Peter~Krusche, Alexander~Tiskin et~al.~// \BibEmph{The Plant Journal}.
  \BibDash
\newblock 2010. \BibDash
\newblock Vol.~64, no.~1. \BibDash
\newblock P.~165--176.

\bibitem{aggarwal1987geometric}
\selectlanguageifdefined{english}
Geometric applications of a matrix-searching algorithm~/ Alok~Aggarwal,
  Maria~M~Klawe, Shlomo~Moran et~al.~// \BibEmph{Algorithmica}. \BibDash
\newblock 1987. \BibDash
\newblock Vol.~2, no. 1-4. \BibDash
\newblock P.~195--208.

\bibitem{horie2010tool}
\selectlanguageifdefined{english}
\BibEmph{Horie~Michihiro, Chiba~Shigeru}. Tool support for crosscutting
  concerns of API documentation~// Proceedings of the 9th International
  Conference on Aspect-Oriented Software Development. \BibDash
\newblock 2010. \BibDash
\newblock P.~97--108.

\bibitem{huang1994global}
\selectlanguageifdefined{english}
\BibEmph{Huang~Xiaoqui}. On global sequence alignment~//
  \BibEmph{Bioinformatics}. \BibDash
\newblock 1994. \BibDash
\newblock Vol.~10, no.~3. \BibDash
\newblock P.~227--235.

\bibitem{luciv2019interactive}
\selectlanguageifdefined{english}
Interactive Duplicate Search in Software Documentation~/ DV~Luciv, DV~Koznov,
  AA~Shelikhovskii et~al.~// \BibEmph{arXiv preprint arXiv:1908.08266}.
  \BibDash
\newblock 2019.

\bibitem{kipyegen2013importance}
\selectlanguageifdefined{english}
\BibEmph{Kipyegen~Noela~Jemutai, Korir~William~PK}. Importance of software
  documentation~// \BibEmph{International Journal of Computer Science Issues
  (IJCSI)}. \BibDash
\newblock 2013. \BibDash
\newblock Vol.~10, no.~5. \BibDash
\newblock P.~223.

\bibitem{koznov2017duplicate}
\selectlanguageifdefined{english}
\BibEmph{Koznov~DV, Luciv~DV, Chernishev~GA}. Duplicate management in software
  documentation maintenance~// CEUR Workshop Proceedings~/ RWTH Aahen
  University. \BibDash
\newblock Vol.~1989. \BibDash
\newblock 2017. \BibDash
\newblock P.~195--201.

\bibitem{krusche2009parallel}
\selectlanguageifdefined{english}
\BibEmph{Krusche~Peter, Tiskin~Alexander}. Parallel longest increasing
  subsequences in scalable time and memory~// International Conference on
  Parallel Processing and Applied Mathematics~/ Springer. \BibDash
\newblock 2009. \BibDash
\newblock P.~176--185.

\bibitem{luciv2016fuzzy}
\selectlanguageifdefined{english}
On fuzzy repetitions detection in documentation reuse~/ DV~Luciv, DV~Koznov,
  Hamid~Abdul~Basit, Andrey~N~Terekhov~// \BibEmph{Programming and Computer
  Software}. \BibDash
\newblock 2016. \BibDash
\newblock Vol.~42, no.~4. \BibDash
\newblock P.~216--224.

\bibitem{plosch2014value}
\selectlanguageifdefined{english}
\BibEmph{Pl{\"o}sch~Reinhold, Dautovic~Andreas, Saft~Matthias}. The value of
  software documentation quality~// 2014 14th International Conference on
  Quality Software~/ IEEE. \BibDash
\newblock 2014. \BibDash
\newblock P.~333--342.

\bibitem{poruban2014reusable}
\selectlanguageifdefined{english}
\BibEmph{Porub{\"a}n~Jaroslav et~al.} Reusable software documentation with
  phrase annotations~// \BibEmph{Central European Journal of Computer Science}.
  \BibDash
\newblock 2014. \BibDash
\newblock Vol.~4, no.~4. \BibDash
\newblock P.~242--258.

\bibitem{poruban2016preliminary}
\selectlanguageifdefined{english}
\BibEmph{Porub{\"a}n~Jaroslav et~al.} Preliminary report on empirical study of
  repeated fragments in internal documentation~// 2016 Federated Conference on
  Computer Science and Information Systems (FedCSIS)~/ IEEE. \BibDash
\newblock 2016. \BibDash
\newblock P.~1573--1576.

\bibitem{rago2016identifying}
\selectlanguageifdefined{english}
\BibEmph{Rago~Alejandro, Marcos~Claudia, Diaz-Pace~J~Andres}. Identifying
  duplicate functionality in textual use cases by aligning semantic actions~//
  \BibEmph{Software \& Systems Modeling}. \BibDash
\newblock 2016. \BibDash
\newblock Vol.~15, no.~2. \BibDash
\newblock P.~579--603.

\bibitem{soto2015similarity}
\selectlanguageifdefined{english}
Similarity-based support for text reuse in technical writing~/ Axel~J~Soto,
  Abidalrahman~Mohammad, Andrew~Albert et~al.~// Proceedings of the 2015 ACM
  Symposium on Document Engineering. \BibDash
\newblock 2015. \BibDash
\newblock P.~97--106.

\bibitem{tiskin2006all}
\selectlanguageifdefined{english}
\BibEmph{Tiskin~Alexander}. All semi-local longest common subsequences in
  subquadratic time~// International Computer Science Symposium in Russia~/
  Springer. \BibDash
\newblock 2006. \BibDash
\newblock P.~352--363.

\bibitem{tiskin2006longest}
\selectlanguageifdefined{english}
\BibEmph{Tiskin~Alexander}. Longest common subsequences in permutations and
  maximum cliques in circle graphs~// Annual Symposium on Combinatorial Pattern
  Matching~/ Springer. \BibDash
\newblock 2006. \BibDash
\newblock P.~270--281.

\bibitem{alex2007semilocal}
\selectlanguageifdefined{english}
\BibEmph{Tiskin~Alexander}. Semi-local string comparison: algorithmic
  techniques and applications. \BibDash
\newblock 2007. \BibDash
\newblock 0707.3619.

\bibitem{tiskin2008semi}
\selectlanguageifdefined{english}
\BibEmph{Tiskin~Alexander}. Semi-local string comparison: Algorithmic
  techniques and applications~// \BibEmph{Mathematics in Computer Science}.
  \BibDash
\newblock 2008. \BibDash
\newblock Vol.~1, no.~4. \BibDash
\newblock P.~571--603.

\bibitem{tiskin2011towards}
\selectlanguageifdefined{english}
\BibEmph{Tiskin~Alexander}. Towards approximate matching in compressed strings:
  Local subsequence recognition~// International Computer Science Symposium in
  Russia~/ Springer. \BibDash
\newblock 2011. \BibDash
\newblock P.~401--414.

\bibitem{tiskin2015fast}
\selectlanguageifdefined{english}
\BibEmph{Tiskin~Alexander}. Fast distance multiplication of unit-Monge
  matrices~// \BibEmph{Algorithmica}. \BibDash
\newblock 2015. \BibDash
\newblock Vol.~71, no.~4. \BibDash
\newblock P.~859--888.

\bibitem{tiskin2019bounded}
\selectlanguageifdefined{english}
\BibEmph{Tiskin~Alexander}. Bounded-Length Smith-Waterman Alignment~// 19th
  International Workshop on Algorithms in Bioinformatics (WABI 2019)~/ Schloss
  Dagstuhl-Leibniz-Zentrum fuer Informatik. \BibDash
\newblock 2019.

\bibitem{tofigh2009optimum}
\selectlanguageifdefined{english}
\BibEmph{Tofigh~Ali}. Optimum branchings and spanning aborescences~//
  \BibEmph{Advanced Algorithms course notes, Sep}. \BibDash
\newblock 2009.

\end{thebibliography}
