\begin{thebibliography}{10}
\def\selectlanguageifdefined#1{
\expandafter\ifx\csname date#1\endcsname\relax
\else\selectlanguage{#1}\fi}
\providecommand*{\href}[2]{{\small #2}}
\providecommand*{\url}[1]{{\small #1}}
\providecommand*{\BibUrl}[1]{\url{#1}}
\providecommand{\BibAnnote}[1]{}
\providecommand*{\BibEmph}[1]{#1}
\ProvideTextCommandDefault{\cyrdash}{\iflanguage{russian}{\hbox
  to.8em{--\hss--}}{\textemdash}}
\providecommand*{\BibDash}{\ifdim\lastskip>0pt\unskip\nobreak\hskip.2em plus
  0.1em\fi
\cyrdash\hskip.2em plus 0.1em\ignorespaces}
\renewcommand{\newblock}{\ignorespaces}

\bibitem{graph-propery-model}
\selectlanguageifdefined{english}
\BibEmph{Angles~Renzo}. The Property Graph Database Model~// AMW. \BibDash
\newblock 2018.

\bibitem{Azimov:2018:CPQ:3210259.3210264}
\selectlanguageifdefined{english}
\BibEmph{Azimov~Rustam, Grigorev~Semyon}.
  \href{http://dx.doi.org/10.1145/3210259.3210264}{Context-Free Path Querying
  by Matrix Multiplication}~// Proceedings of the 1st ACM SIGMOD Joint
  International Workshop on Graph Data Management Experiences \& Systems
  (GRADES) and Network Data Analytics (NDA). \BibDash
\newblock GRADES-NDA ’18. \BibDash
\newblock New York, NY, USA~: Association for Computing Machinery, 2018.
  \BibDash
\newblock Access mode: \BibUrl{https://doi.org/10.1145/3210259.3210264}
  (online; accessed: 29.05.2020).

\bibitem{FLCpathProblem}
\selectlanguageifdefined{english}
\BibEmph{Barrett~Chris, Jacob~Riko, Marathe~Madhav}.
  Formal-Language-Constrained Path Problems~//
  \href{http://dx.doi.org/10.1137/S0097539798337716}{\BibEmph{SIAM J. Comput.}}
  \BibDash
\newblock 2000. \BibDash May. \BibDash
\newblock Vol.~30, no.~3. \BibDash
\newblock P.~809–837. \BibDash
\newblock Access mode: \BibUrl{https://doi.org/10.1137/S0097539798337716}
  (online; accessed: 29.05.2020).

\bibitem{cfpq-data}
\selectlanguageifdefined{english}
CFPQ\_Data. Graphs and grammars for experimental analysis of context-free path
  querying algorithms. \BibDash
\newblock Access mode:
  \BibUrl{https://github.com/JetBrains-Research/CFPQ\_Data} (online; accessed:
  29.05.2020).

\bibitem{zhlang-2016}
\selectlanguageifdefined{english}
Context-free path queries on RDF graphs~/ X.~Zhang, Z.~Feng, X.~Wang et~al.~//
  International Semantic Web Conference~/ Springer. \BibDash
\newblock 2016. \BibDash
\newblock P.~632--648.

\bibitem{cypher-language}
\selectlanguageifdefined{english}
\href{http://dx.doi.org/10.1145/3183713.3190657}{Cypher: An Evolving Query
  Language for Property Graphs}~/ Nadime~Francis, Andrés~Taylor,
  Alastair~Green et~al. \BibDash
\newblock 2018. \BibDash 05. \BibDash
\newblock P.~1433--1445.

\bibitem{cypher-specification}
\selectlanguageifdefined{english}
Cypher extention. CIP2017-02-06 Path Patterns. \BibDash
\newblock Access mode:
  \BibUrl{https://github.com/thobe/openCypher/blob/rpq/cip/1.accepted/CIP2017-02-06-Path-Patterns.adoc}
  (online; accessed: 29.05.2020).

\bibitem{docker}
\selectlanguageifdefined{english}
Docker containter with RedisGraph fork. Context-free path queries support.
  \BibDash
\newblock Access mode: \BibUrl{https://hub.docker.com/r/simpletondl/redisgraph}
  (online; accessed: 29.05.2020).

\bibitem{azimov-evalution}
\selectlanguageifdefined{english}
\href{http://dx.doi.org/10.1145/3327964.3328503}{Evaluation of the Context-Free
  Path Querying Algorithm Based on Matrix Multiplication}~/ Nikita~Mishin,
  Iaroslav~Sokolov, Egor~Spirin et~al.~// Proceedings of the 2nd Joint
  International Workshop on Graph Data Management Experiences \& Systems
  (GRADES) and Network Data Analytics (NDA). \BibDash
\newblock GRADES-NDA’19. \BibDash
\newblock New York, NY, USA~: Association for Computing Machinery, 2019.
  \BibDash
\newblock Access mode: \BibUrl{https://doi.org/10.1145/3327964.3328503}.

\bibitem{Kuijpers:2019:ESC:3335783.3335791}
\selectlanguageifdefined{english}
\href{http://dx.doi.org/10.1145/3335783.3335791}{An Experimental Study of
  Context-Free Path Query Evaluation Methods}~/ Jochem~Kuijpers,
  George~Fletcher, Nikolay~Yakovets, Tobias~Lindaaker~// Proceedings of the
  31st International Conference on Scientific and Statistical Database
  Management. \BibDash
\newblock SSDBM '19. \BibDash
\newblock New York, NY, USA~: ACM, 2019. \BibDash
\newblock P.~121--132. \BibDash
\newblock Access mode: \BibUrl{http://doi.acm.org/10.1145/3335783.3335791}
  (online; accessed: 29.05.2020).

\bibitem{hellings-2015}
\selectlanguageifdefined{english}
\BibEmph{Hellings~Jelle}. Querying for Paths in Graphs using Context-Free Path
  Queries~// \BibEmph{arXiv preprint arXiv:1502.02242}. \BibDash
\newblock 2015.

\bibitem{graph-blas}
\selectlanguageifdefined{english}
\BibEmph{Jeremy~Kepner}. GraphBLAS Mathematics - Provisional Release 1.0.
  \BibDash
\newblock 2017. \BibDash
\newblock Access mode:
  \BibUrl{http://www.mit.edu/~kepner/GraphBLAS/GraphBLAS-Math-release.pdf}
  (online; accessed: 29.05.2020).

\bibitem{datascince-lifecycle}
\selectlanguageifdefined{english}
\BibEmph{Miao~Hui, Deshpande~Amol}. Understanding Data Science Lifecycle
  Provenance via Graph Segmentation and Summarization~// \BibEmph{2019 IEEE
  35th International Conference on Data Engineering (ICDE)}. \BibDash
\newblock 2019. \BibDash
\newblock P.~1710--1713.

\bibitem{neo4j}
\selectlanguageifdefined{english}
Neo4j. \BibDash
\newblock Access mode: \BibUrl{https://neo4j.com} (online; accessed:
  29.05.2020).

\bibitem{parser-combinators}
\selectlanguageifdefined{english}
\href{http://dx.doi.org/10.1145/3241653.3241655}{Parser Combinators for
  Context-Free Path Querying}~/ Ekaterina~Verbitskaia, Ilya~Kirillov,
  Ilya~Nozkin, Semyon~Grigorev~// Proceedings of the 9th ACM SIGPLAN
  International Symposium on Scala. \BibDash
\newblock Scala 2018. \BibDash
\newblock New York, NY, USA~: Association for Computing Machinery, 2018.
  \BibDash
\newblock P.~13–--23. \BibDash
\newblock Access mode: \BibUrl{https://doi.org/10.1145/3241653.3241655}
  (online; accessed: 29.05.2020).

\bibitem{geospices}
\selectlanguageifdefined{english}
\BibEmph{Peter~DeVries}. The GeoSpecies Knowledge Base ontology. \BibDash
\newblock 2009. \BibDash
\newblock Access mode: \BibUrl{http://rdf.geospecies.org/geospecies.rdf.gz}
  (online; accessed: 29.05.2020).

\bibitem{redis}
\selectlanguageifdefined{english}
Redis. Open source (BSD licensed), in-memory data structure store. \BibDash
\newblock Access mode: \BibUrl{https://redis.io} (online; accessed:
  29.05.2020).

\bibitem{redis-graph}
\selectlanguageifdefined{english}
RedisGraph. Graph database module for Redis. \BibDash
\newblock Access mode: \BibUrl{https://oss.redislabs.com/redisgraph} (online;
  accessed: 29.05.2020).

\bibitem{github}
\selectlanguageifdefined{english}
RedisGraph fork. Context-free path queries support. \BibDash
\newblock Access mode:
  \BibUrl{https://github.com/YaccConstructor/RedisGraph/tree/path_patterns}
  (online; accessed: 29.05.2020).

\bibitem{santos-2018}
\selectlanguageifdefined{english}
\BibEmph{Santos~Fred~C., Costa~Umberto~S., Musicante~Martin~A.} A Bottom-Up
  Algorithm for Answering Context-Free Path Queries in Graph Databases~// Web
  Engineering~/ Ed.\ by\ Tommi~Mikkonen, Ralf~Klamma, Juan~Hern{\'a}ndez.
  \BibDash
\newblock Cham~: Springer International Publishing, 2018. \BibDash
\newblock P.~225--233.

\bibitem{bio-application}
\selectlanguageifdefined{English}
\BibEmph{Sevon~Petteri, Eronen~Lauri}. Subgraph queries by context-free
  grammars~// \BibEmph{Journal of Integrative Bioinformatics : JIB}. \BibDash
\newblock 2008. \BibDash
\newblock Vol.~5, no. 100, 16 s.

\bibitem{suite-sparse}
\selectlanguageifdefined{english}
SuiteSparse. A suite of sparse matrix software. \BibDash
\newblock Access mode: \BibUrl{http://faculty.cse.tamu.edu/davis} (online;
  accessed: 29.05.2020).

\end{thebibliography}
