\algtext*{EndWhile}% Remove "end while" text
\algtext*{EndIf}% Remove "end if" text
\algtext*{EndFor}% Remove "end for" text
\algtext*{EndFunction}% Remove "end function" text

\title{Синтаксический анализ регулярных множеств}

\titlerunning{Синтаксический анализ регулярных множеств}

\author{Вербицкая Екатерина Андреевна}

\authorrunning{Е.А.Вербицкая}

\tocauthor{Е.А.Вербицкая}
\institute{Санкт-Петербургский государственный университет\\
\email{kajigor@gmail.com}}

\maketitle             

\begin{abstract}
test
\end{abstract}

\input{Verbitskaya/introduction}
\input{Verbitskaya/statement}
\input{Verbitskaya/relatedworks}
\input{Verbitskaya/algorithm}
\input{Verbitskaya/correctness}
\input{Verbitskaya/evaluation}
\input{Verbitskaya/conclusion}

\begin{thebibliography}{99}
\bibitem{Alvor}
  A.Annamaa, A.Breslav, J.Kabanov, V.Vene.
  An Interactive Tool for Analyzing Embedded SQL Queries //
  Programming Languages and Systems, 2010, P.~131--138.

\bibitem{Alvor2}
  A.Annamaa, A.Breslav, V.Vene.
  Using Abstract Lexical Analysis and Parsing to Detect Errors in String-Embedded DSL Statements //
  Proceedings of the 22nd Nordic Workshop on Programming Theory, 2010, P.~20--22.

\bibitem{DSQLISO}
  Information technology --- Database languages --- SQL. ISO. ISO/IEC 9075:1992, 1992.

\bibitem{JSP}
  D.Houglan, A.Tavistock. Core JSP. Prentice Hall PTR, 2000.

\bibitem{PHPmySQL}
  PHP mySQL interface. \url{http://php.net/manual/en/mysqli.query.php}.

\bibitem{SPPF}
  J.Rekers. Parser Generation for Interactive Environments, 1992.

\bibitem{LangInclusion}
  P.R.J.Asveld, A.Nijholt, Anton.
  The Inclusion Problem for Some Subclasses of Context-free Languages /
  Theoretical Computer Science, Vol.~230, \textnumero~1--2, 1999.

\bibitem{Stranger}
 F.Yu, M.Alkhalaf, T.Bultan, O.H.Ibarra.
 Automata-based Symbolic String Analysis for Vulnerability Detection //
 Form. Methods Syst. Des., Vol.~44, \textnumero~1, 2014.

\bibitem{JSA}
 A.S.Christensen, A.M{\o}ller, M.I.Schwartzbach.
 Precise Analysis of String Expressions //
 Proceedings of the International Conference on Static Analysis, 2003.

\bibitem{AbstrParsing}
 K-G.Doh, H.Kim, D.A.Schmidt.
 Abstract Parsing: Static Analysis of Dynamically Generated String Output Using LR-Parsing Technology //
 Proceedings of the International Symposium on Static Analysis, 2009, P.~256--272.

\bibitem{LRAbstrParsing}
 K-G.Doh, H.Kim, D.A.Schmidt, David A.
 Abstract LR-parsing // Formal Modeling, 2011, P.~90--109.

\bibitem{LRAbstrParsingSema}
 K-G.Doh, H.Kim, D.A.Schmidt.
 Static Validation of Dynamically Generated HTML Documents Based on Abstract Parsing and Semantic Processing //
 Proceedings of the International Symposium on Static Analysis, 2013, P.~194--214.

\bibitem{AbstractInterpretation}
 P.Cousot, R.Cousot.
 Abstract Interpretation: a Unified Lattice Model for Static Analysis of Programs by Construction 
 or Approximation of Fixpoints // Conference Record of the Fourth Annual ACM SIGPLAN-SIGACT Symposium on Principles of Programming Languages,
 1977.

\bibitem{Tomita}
 M.Tomitqa. An Efficient Context-free Parsing Algorithm for Natural Languages //
 Proceedings of the 9th International Joint Conference on Artificial Intelligence, 1985, P.~756--764.

\bibitem{SECR13}
 S.Grigorev, I.Kirilenko, Iakov.
 GLR-based Abstract Parsing //
 Proceedings of the 9th Central \&\#38; Eastern European Software Engineering Conference in Russia, 2013, P.~5:1--5:9.

\bibitem{SECR14}
 S.Grigorev, E.Verbitskaia, A.Ivanov, M.Polubelova, E.Mavchun.
 String-embedded Language Support in Integrated Development Environment //
 Proceedings of the 10th Central and Eastern European Software Engineering Conference in Russia, 2014, P.~21:1--21:11.

\bibitem{YC}
 I.Kirilenko, S.Grigorev, D.Avdiukhin.
 Syntax Analyzers Development in Automated Reengineering of Informational System //
 St. Petersburg State Polytechnical University Journal. Computer Science. Telecommunications and Control Systems,
 Vol.~174, \textnumero~3, P.~94--98.

\bibitem{FSharp}
 D.Syme, A.Granicz, A.Cisternino. Expert F\# (Expert's Voice in .Net). Apress, 2011.
\end{thebibliography}
