\begin{thebibliography}{10}
\def\selectlanguageifdefined#1{
\expandafter\ifx\csname date#1\endcsname\relax
\else\selectlanguage{#1}\fi}
\providecommand*{\href}[2]{{\small #2}}
\providecommand*{\url}[1]{{\small #1}}
\providecommand*{\BibUrl}[1]{\url{#1}}
\providecommand{\BibAnnote}[1]{}
\providecommand*{\BibEmph}[1]{#1}
\ProvideTextCommandDefault{\cyrdash}{\iflanguage{russian}{\hbox
  to.8em{--\hss--}}{\textemdash}}
\providecommand*{\BibDash}{\ifdim\lastskip>0pt\unskip\nobreak\hskip.2em plus
  0.1em\fi
\cyrdash\hskip.2em plus 0.1em\ignorespaces}
\renewcommand{\newblock}{\ignorespaces}

\bibitem{FndDB}
\selectlanguageifdefined{english}
\BibEmph{Abiteboul~Serge, Hull~Richard, Vianu~Victor}. Foundations of
  databases: the logical level. \BibDash
\newblock Addison-Wesley Longman Publishing Co., Inc., 1995.

\bibitem{abiteboul1997regular}
\selectlanguageifdefined{english}
\BibEmph{Abiteboul~Serge, Vianu~Victor}. Regular path queries with
  constraints~// Proceedings of the sixteenth ACM SIGACT-SIGMOD-SIGART
  symposium on Principles of database systems~/ ACM. \BibDash
\newblock 1997. \BibDash
\newblock P.~122--133.

\bibitem{fan2011adding}
\selectlanguageifdefined{english}
Adding regular expressions to graph reachability and pattern queries~/
  Wenfei~Fan, Jianzhong~Li, Shuai~Ma et~al.~// Data Engineering (ICDE), 2011
  IEEE 27th International Conference on~/ IEEE. \BibDash
\newblock 2011. \BibDash
\newblock P.~39--50.

\bibitem{barrett2000formal}
\selectlanguageifdefined{english}
\BibEmph{Barrett~Chris, Jacob~Riko, Marathe~Madhav}.
  Formal-language-constrained path problems~// \BibEmph{SIAM Journal on
  Computing}. \BibDash
\newblock 2000. \BibDash
\newblock Vol.~30, no.~3. \BibDash
\newblock P.~809--837.

\bibitem{bastani2015specification}
\selectlanguageifdefined{english}
\BibEmph{Bastani~Osbert, Anand~Saswat, Aiken~Alex}. Specification inference
  using context-free language reachability~// ACM SIGPLAN Notices~/ ACM.
  \BibDash
\newblock Vol.~50. \BibDash
\newblock 2015. \BibDash
\newblock P.~553--566.

\bibitem{matricesOnGPGPU}
\selectlanguageifdefined{english}
\BibEmph{Che~Shuai, Beckmann~Bradford~M, Reinhardt~Steven~K}. Programming GPGPU
  Graph Applications with Linear Algebra Building Blocks~//
  \BibEmph{International Journal of Parallel Programming}. \BibDash
\newblock 2016. \BibDash
\newblock P.~1--23.

\bibitem{choi1994pumma}
\selectlanguageifdefined{english}
\BibEmph{Choi~Jaeyoung, Walker~David~W, Dongarra~Jack~J}. PUMMA: Parallel
  universal matrix multiplication algorithms on distributed memory concurrent
  computers~// \BibEmph{Concurrency and Computation: Practice and Experience}.
  \BibDash
\newblock 1994. \BibDash
\newblock Vol.~6, no.~7. \BibDash
\newblock P.~543--570.

\bibitem{chomsky}
\selectlanguageifdefined{english}
\BibEmph{Chomsky~Noam}. On certain formal properties of grammars~//
  \BibEmph{Information and control}. \BibDash
\newblock 1959. \BibDash
\newblock Vol.~2, no.~2. \BibDash
\newblock P.~137--167.

\bibitem{RDF}
\selectlanguageifdefined{english}
Context-free path queries on RDF graphs~/ X.~Zhang, Z.~Feng, X.~Wang et~al.~//
  International Semantic Web Conference~/ Springer. \BibDash
\newblock 2016. \BibDash
\newblock P.~632--648.

\bibitem{zhang2013fast}
\selectlanguageifdefined{english}
Fast algorithms for Dyck-CFL-reachability with applications to alias analysis~/
  Qirun~Zhang, Michael~R~Lyu, Hao~Yuan, Zhendong~Su~// ACM SIGPLAN Notices~/
  ACM. \BibDash
\newblock Vol.~48. \BibDash
\newblock 2013. \BibDash
\newblock P.~435--446.

\bibitem{GLL}
\selectlanguageifdefined{english}
\BibEmph{Grigorev~Semyon, Ragozina~Anastasiya}. Context-Free Path Querying with
  Structural Representation of Result~// \BibEmph{arXiv preprint
  arXiv:1612.08872}. \BibDash
\newblock 2016.

\bibitem{Grune}
\selectlanguageifdefined{english}
\BibEmph{Grune~Dick, Jacobs~Ceriel J.~H.} Parsing Techniques (Monographs in
  Computer Science). \BibDash
\newblock Secaucus, NJ, USA~: Springer-Verlag New York, Inc., 2006. \BibDash
\newblock
  ISBN:~\href{http://isbndb.com/search-all.html?kw=038720248X}{038720248X}.

\bibitem{hellingsRelational}
\selectlanguageifdefined{english}
\BibEmph{Hellings~J.} Conjunctive context-free path queries. \BibDash
\newblock 2014.

\bibitem{hellingsPathQuerying}
\selectlanguageifdefined{english}
\BibEmph{Hellings~Jelle}. Querying for Paths in Graphs using Context-Free Path
  Queries~// \BibEmph{arXiv preprint arXiv:1502.02242}. \BibDash
\newblock 2015.

\bibitem{kasami}
\selectlanguageifdefined{english}
AN EFFICIENT RECOGNITION AND SYNTAXANALYSIS ALGORITHM FOR CONTEXT-FREE
  LANGUAGES.~: Rep.~/ DTIC Document~; Executor: Tadao~Kasami~: 1965.

\bibitem{apspGPU}
\selectlanguageifdefined{english}
\BibEmph{Katz~Gary~J, Kider~Jr~Joseph~T}. All-pairs shortest-paths for large
  graphs on the GPU~// Proceedings of the 23rd ACM SIGGRAPH/EUROGRAPHICS
  symposium on Graphics hardware~/ Eurographics Association. \BibDash
\newblock 2008. \BibDash
\newblock P.~47--55.

\bibitem{kodumal2004set}
\selectlanguageifdefined{english}
\BibEmph{Kodumal~John, Aiken~Alex}. The set constraint/CFL reachability
  connection in practice~// \BibEmph{ACM Sigplan Notices}. \BibDash
\newblock 2004. \BibDash
\newblock Vol.~39, no.~6. \BibDash
\newblock P.~207--218.

\bibitem{graphDB}
\selectlanguageifdefined{english}
\BibEmph{Mendelzon~A., Wood~P.} Finding Regular Simple Paths in Graph
  Databases~// \BibEmph{SIAM J. Computing}. \BibDash
\newblock 1995. \BibDash
\newblock Vol.~24, no.~6. \BibDash
\newblock P.~1235--1258.

\bibitem{nole2016regular}
\selectlanguageifdefined{english}
\BibEmph{Nol{\'e}~Maurizio, Sartiani~Carlo}. Regular path queries on massive
  graphs~// Proceedings of the 28th International Conference on Scientific and
  Statistical Database Management~/ ACM. \BibDash
\newblock 2016. \BibDash
\newblock P.~13.

\bibitem{okhotin2001conjunctive}
\selectlanguageifdefined{english}
\BibEmph{Okhotin~Alexander}. Conjunctive grammars~// \BibEmph{Journal of
  Automata, Languages and Combinatorics}. \BibDash
\newblock 2001. \BibDash
\newblock Vol.~6, no.~4. \BibDash
\newblock P.~519--535.

\bibitem{okhotinBoolean}
\selectlanguageifdefined{english}
\BibEmph{Okhotin~Alexander}. Boolean grammars~// \BibEmph{Information and
  Computation}. \BibDash
\newblock 2004. \BibDash
\newblock Vol. 194, no.~1. \BibDash
\newblock P.~19--48.

\bibitem{okhotinConjAndBool}
\selectlanguageifdefined{english}
\BibEmph{Okhotin~Alexander}. Conjunctive and Boolean grammars: the true general
  case of the context-free grammars~// \BibEmph{Computer Science Review}.
  \BibDash
\newblock 2013. \BibDash
\newblock Vol.~9. \BibDash
\newblock P.~27--59.

\bibitem{okhotin_cyk}
\selectlanguageifdefined{english}
\BibEmph{Okhotin~Alexander}. Parsing by matrix multiplication generalized to
  Boolean grammars~// \BibEmph{Theoretical Computer Science}. \BibDash
\newblock 2014. \BibDash
\newblock Vol. 516. \BibDash
\newblock P.~101--120.

\bibitem{Bio}
\selectlanguageifdefined{english}
Quantifying variances in comparative RNA secondary structure prediction~/
  James~WJ~Anderson, {\'A}d{\'a}m~Nov{\'a}k, Zsuzsanna~S{\"u}k{\"o}sd et~al.~//
  \BibEmph{BMC bioinformatics}. \BibDash
\newblock 2013. \BibDash
\newblock Vol.~14, no.~1. \BibDash
\newblock P.~149.

\bibitem{reps1998program}
\selectlanguageifdefined{english}
\BibEmph{Reps~Thomas}. Program analysis via graph reachability~//
  \BibEmph{Information and software technology}. \BibDash
\newblock 1998. \BibDash
\newblock Vol.~40, no.~11. \BibDash
\newblock P.~701--726.

\bibitem{reutter2017regular}
\selectlanguageifdefined{english}
\BibEmph{Reutter~Juan~L, Romero~Miguel, Vardi~Moshe~Y}. Regular queries on
  graph databases~// \BibEmph{Theory of Computing Systems}. \BibDash
\newblock 2017. \BibDash
\newblock Vol.~61, no.~1. \BibDash
\newblock P.~31--83.

\bibitem{scott2010gll}
\selectlanguageifdefined{english}
\BibEmph{Scott~Elizabeth, Johnstone~Adrian}. GLL parsing~// \BibEmph{Electronic
  Notes in Theoretical Computer Science}. \BibDash
\newblock 2010. \BibDash
\newblock Vol. 253, no.~7. \BibDash
\newblock P.~177--189.

\bibitem{GraphQueryWithEarley}
\selectlanguageifdefined{english}
\BibEmph{Sevon~Petteri, Eronen~Lauri}. Subgraph queries by context-free
  grammars~// \BibEmph{Journal of Integrative Bioinformatics}. \BibDash
\newblock 2008. \BibDash
\newblock Vol.~5, no.~2. \BibDash
\newblock P.~100.

\bibitem{hetero_multi-GPU}
\selectlanguageifdefined{english}
\BibEmph{Song~Fengguang, Tomov~Stanimire, Dongarra~Jack}. Enabling and scaling
  matrix computations on heterogeneous multi-core and multi-GPU systems~//
  Proceedings of the 26th ACM international conference on Supercomputing~/ ACM.
  \BibDash
\newblock 2012. \BibDash
\newblock P.~365--376.

\bibitem{fsharp}
\selectlanguageifdefined{english}
\BibEmph{Syme~Don, Granicz~Adam, Cisternino~Antonio}. Expert F\# 3.0. \BibDash
\newblock Springer, 2012.

\bibitem{valiant}
\selectlanguageifdefined{english}
\BibEmph{Valiant~Leslie~G}. General context-free recognition in less than cubic
  time~// \BibEmph{Journal of computer and system sciences}. \BibDash
\newblock 1975. \BibDash
\newblock Vol.~10, no.~2. \BibDash
\newblock P.~308--315.

\bibitem{xu2009scaling}
\selectlanguageifdefined{english}
\BibEmph{Xu~Guoqing, Rountev~Atanas, Sridharan~Manu}. Scaling
  CFL-reachability-based points-to analysis using context-sensitive
  must-not-alias analysis~// ECOOP~/ Springer. \BibDash
\newblock Vol.~9. \BibDash
\newblock 2009. \BibDash
\newblock P.~98--122.

\bibitem{transitive-closure}
\selectlanguageifdefined{english}
\BibEmph{Yannakakis~Mihalis}. Graph-theoretic methods in database theory~//
  Proceedings of the ninth ACM SIGACT-SIGMOD-SIGART symposium on Principles of
  database systems~/ ACM. \BibDash
\newblock 1990. \BibDash
\newblock P.~230--242.

\bibitem{younger}
\selectlanguageifdefined{english}
\BibEmph{Younger~Daniel~H}. Recognition and parsing of context-free languages
  in time n3~// \BibEmph{Information and control}. \BibDash
\newblock 1967. \BibDash
\newblock Vol.~10, no.~2. \BibDash
\newblock P.~189--208.

\bibitem{MM_on_multi-GPU}
\selectlanguageifdefined{english}
\BibEmph{Zhang~Peng, Gao~Yuxiang}. Matrix multiplication on high-density
  multi-GPU architectures: theoretical and experimental investigations~//
  International Conference on High Performance Computing~/ Springer. \BibDash
\newblock 2015. \BibDash
\newblock P.~17--30.

\bibitem{zhang2017context}
\selectlanguageifdefined{english}
\BibEmph{Zhang~Qirun, Su~Zhendong}. Context-sensitive data-dependence analysis
  via linear conjunctive language reachability~// Proceedings of the 44th ACM
  SIGPLAN Symposium on Principles of Programming Languages~/ ACM. \BibDash
\newblock 2017. \BibDash
\newblock P.~344--358.

\end{thebibliography}
