\begin{thebibliography}{32}
\def\selectlanguageifdefined#1{
\expandafter\ifx\csname date#1\endcsname\relax
\else\selectlanguage{#1}\fi}
\providecommand*{\href}[2]{{\small #2}}
\providecommand*{\url}[1]{{\small #1}}
\providecommand*{\BibUrl}[1]{\url{#1}}
\providecommand{\BibAnnote}[1]{}
\providecommand*{\BibEmph}[1]{#1}
\ProvideTextCommandDefault{\cyrdash}{\iflanguage{russian}{\hbox
  to.8em{--\hss--}}{\textemdash}}
\providecommand*{\BibDash}{\ifdim\lastskip>0pt\unskip\nobreak\hskip.2em plus
  0.1em\fi
\cyrdash\hskip.2em plus 0.1em\ignorespaces}
\renewcommand{\newblock}{\ignorespaces}

\bibitem{andersen1994program}
\selectlanguageifdefined{english}
\BibEmph{Andersen~Lars~Ole}. Program analysis and specialization for the C
  programming language~: Ph.\,D. thesis~/ Lars~Ole~Andersen~; University of
  Cophenhagen. \BibDash
\newblock 1994.

\bibitem{barrett1998decision}
\selectlanguageifdefined{english}
\BibEmph{Barrett~Clark~W, Dill~David~L, Levitt~Jeremy~R}. A decision procedure
  for bit-vector arithmetic~// Proceedings 1998 Design and Automation
  Conference. 35th DAC.(Cat. No. 98CH36175)~/ IEEE. \BibDash
\newblock 1998. \BibDash
\newblock P.~522--527.

\bibitem{beyer2015software}
\selectlanguageifdefined{english}
\BibEmph{Beyer~Dirk}. \textit{Software verification and verifiable
  witnesses}~// International Conference on Tools and Algorithms for the
  Construction and Analysis of Systems~/ Springer. \BibDash
\newblock 2015. \BibDash
\newblock P.~401--416.

\bibitem{beyer2016reliable}
\selectlanguageifdefined{english}
\BibEmph{Beyer~Dirk}. \textit{Reliable and reproducible competition results
  with benchexec and witnesses (report on SV-COMP 2016)}~// International
  Conference on Tools and Algorithms for the Construction and Analysis of
  Systems~/ Springer. \BibDash
\newblock 2016. \BibDash
\newblock P.~887--904.

\bibitem{beyer2017software}
\selectlanguageifdefined{english}
\BibEmph{Beyer~Dirk}. \textit{Software verification with validation of
  results}~// International Conference on Tools and Algorithms for the
  Construction and Analysis of Systems~/ Springer. \BibDash
\newblock 2017. \BibDash
\newblock P.~331--349.

\bibitem{bohme2011heaps}
\selectlanguageifdefined{english}
\BibEmph{B{\"o}hme~Sascha, Moskal~Micha{\l}}. Heaps and data structures: A
  challenge for automated provers~// International Conference on Automated
  Deduction~/ Springer. \BibDash
\newblock 2011. \BibDash
\newblock P.~177--191.

\bibitem{bornat2000proving}
\selectlanguageifdefined{english}
\BibEmph{Bornat~Richard}. Proving pointer programs in Hoare logic~//
  International Conference on Mathematics of Program Construction~/ Springer.
  \BibDash
\newblock 2000. \BibDash
\newblock P.~102--126.

\bibitem{cousot1992abstract}
\selectlanguageifdefined{english}
\BibEmph{Cousot~Patrick, Cousot~Radhia}. Abstract interpretation and
  application to logic programs~// \BibEmph{The Journal of Logic Programming}.
  \BibDash
\newblock 1992. \BibDash
\newblock Vol.~13, no. 2-3. \BibDash
\newblock P.~103--179.

\bibitem{de2008z3}
\selectlanguageifdefined{english}
\BibEmph{De~Moura~Leonardo, Bj{\o}rner~Nikolaj}. \textit{Z3: An efficient SMT
  solver}~// International conference on Tools and Algorithms for the
  Construction and Analysis of Systems~/ Springer. \BibDash
\newblock 2008. \BibDash
\newblock P.~337--340.

\bibitem{dudka2013byte}
\selectlanguageifdefined{english}
\BibEmph{Dudka~Kamil, Peringer~Petr, Vojnar~Tom{\'a}{\v{s}}}.
  \textit{Byte-precise verification of low-level list manipulation}~//
  International Static Analysis Symposium~/ Springer. \BibDash
\newblock 2013. \BibDash
\newblock P.~215--237.

\bibitem{ecmatg3}
\selectlanguageifdefined{english}
\BibEmph{Ecma~TC39}. TG3. Common Language Infrastructure (CLI). Standard
  ECMA-335, June 2005.

\bibitem{wenenhancing}
\selectlanguageifdefined{english}
Enhancing Symbolic Execution by Machine Learning Based Solver Selection~/
  Sheng-Han~Wen, Wei-Loon~Mow, Wei-Ning~Chen et~al.

\bibitem{godel1931formal}
\selectlanguageifdefined{english}
\BibEmph{G{\"o}del~Kurt}. {\"U}ber formal unentscheidbare S{\"a}tze der
  Principia Mathematica und verwandter Systeme I~// \BibEmph{Monatshefte
  f{\"u}r mathematik und physik}. \BibDash
\newblock 1931. \BibDash
\newblock Vol.~38, no.~1. \BibDash
\newblock P.~173--198.

\bibitem{hubert2007separation}
\selectlanguageifdefined{english}
\BibEmph{Hubert~Thierry, March{\'e}~Claude}. Separation analysis for deductive
  verification~// \BibEmph{Heap Analysis and Verification (HAV’07)}. \BibDash
\newblock 2007. \BibDash
\newblock P.~81--93.

\bibitem{khurshid2003generalized}
\selectlanguageifdefined{english}
\BibEmph{Khurshid~Sarfraz, P{\u{a}}s{\u{a}}reanu~Corina~S, Visser~Willem}.
  Generalized symbolic execution for model checking and testing~//
  International Conference on Tools and Algorithms for the Construction and
  Analysis of Systems~/ Springer. \BibDash
\newblock 2003. \BibDash
\newblock P.~553--568.

\bibitem{kolawa1998method}
\selectlanguageifdefined{english}
\BibEmph{Kolawa~Adam~K, Salvador~Roman}. \textit{Method and system for
  generating a computer program test suite using dynamic symbolic execution of
  Java programs}. \BibDash
\newblock 1998. \BibDash
\newblock US Patent 5,784,553.

\bibitem{lahiri2008back}
\selectlanguageifdefined{english}
\BibEmph{Lahiri~Shuvendu, Qadeer~Shaz}. Back to the future: revisiting precise
  program verification using SMT solvers~// ACM SIGPLAN Notices~/ ACM. \BibDash
\newblock Vol.~43. \BibDash
\newblock 2008. \BibDash
\newblock P.~171--182.

\bibitem{mandrykin2017memory}
\selectlanguageifdefined{english}
\BibEmph{Mandrykin~Mikhail, Khoroshilov~Alexey}. A memory model for deductively
  verifying Linux kernel modules~// International Andrei Ershov Memorial
  Conference on Perspectives of System Informatics~/ Springer. \BibDash
\newblock 2017. \BibDash
\newblock P.~256--275.

\bibitem{moy2009automatic}
\selectlanguageifdefined{english}
\BibEmph{Moy~Yannick}. Automatic modular static safety checking for C
  programs~: Ph.\,D. thesis~/ Yannick~Moy~; Paris 11. \BibDash
\newblock 2009.

\bibitem{sethu2018systems}
\selectlanguageifdefined{english}
\BibEmph{Sethu~Ramesh}. \textit{Systems and methods to reverse engineer code to
  models using program analysis and symbolic execution}. \BibDash
\newblock 2018. \BibDash Mar.~22. \BibDash
\newblock US Patent App. 15/268,011.

\bibitem{tarski1998decision}
\selectlanguageifdefined{english}
\BibEmph{Tarski~Alfred}. A decision method for elementary algebra and
  geometry~// Quantifier elimination and cylindrical algebraic decomposition.
  \BibDash
\newblock Springer, 1998. \BibDash
\newblock P.~24--84.

\bibitem{tillmann2008pex}
\selectlanguageifdefined{english}
\BibEmph{Tillmann~Nikolai, de~Halleux~Jonathan}. \textit{Pex--White Box Test
  Generation for. NET}~// \BibEmph{Tests and Proofs}. \BibDash
\newblock 2008. \BibDash
\newblock P.~134--153.

\bibitem{cohen2009vcc}
\selectlanguageifdefined{english}
VCC: A practical system for verifying concurrent C~/ Ernie~Cohen,
  Markus~Dahlweid, Mark~Hillebrand et~al.~// International Conference on
  Theorem Proving in Higher Order Logics~/ Springer. \BibDash
\newblock 2009. \BibDash
\newblock P.~23--42.

\bibitem{cohen2009precise}
\selectlanguageifdefined{english}
A precise yet efficient memory model for C~/ Ernie~Cohen, Micha{\l}~Moskal,
  Stephan~Tobies, Wolfram~Schulte~// \BibEmph{Electronic Notes in Theoretical
  Computer Science}. \BibDash
\newblock 2009. \BibDash
\newblock Vol. 254. \BibDash
\newblock P.~85--103.

\bibitem{beyer2007software}
\selectlanguageifdefined{english}
The software model checker b last~/ Dirk~Beyer, Thomas~A~Henzinger,
  Ranjit~Jhala, Rupak~Majumdar~// \BibEmph{International Journal on Software
  Tools for Technology Transfer}. \BibDash
\newblock 2007. \BibDash
\newblock Vol.~9, no. 5-6. \BibDash
\newblock P.~505--525.

\bibitem{barrett2011cvc4}
\selectlanguageifdefined{english}
\textit{Cvc4}~/ Clark~Barrett, Christopher~L~Conway, Morgan~Deters et~al.~//
  International Conference on Computer Aided Verification~/ Springer. \BibDash
\newblock 2011. \BibDash
\newblock P.~171--177.

\bibitem{wang2017dependence}
\selectlanguageifdefined{english}
\textit{Dependence guided symbolic execution}~/ Haijun~Wang, Ting~Liu,
  Xiaohong~Guan et~al.~// \BibEmph{IEEE Transactions on Software Engineering}.
  \BibDash
\newblock 2017. \BibDash
\newblock Vol.~43, no.~3. \BibDash
\newblock P.~252--271.

\bibitem{yoshida2017klover}
\selectlanguageifdefined{english}
\textit{KLOVER: Automatic Test Generation for C and C Programs, Using Symbolic
  Execution}~/ Hiroaki~Yoshida, Guodong~Li, Takuki~Kamiya et~al.~//
  \BibEmph{IEEE Software}. \BibDash
\newblock 2017. \BibDash
\newblock Vol.~34, no.~5. \BibDash
\newblock P.~30--37.

\bibitem{holik2016predator}
\selectlanguageifdefined{english}
\textit{Predator shape analysis tool suite}~/ Luk{\'a}{\v{s}}~Hol{\'\i}k,
  Michal~Kotoun, Petr~Peringer et~al.~// Haifa Verification Conference~/
  Springer. \BibDash
\newblock 2016. \BibDash
\newblock P.~202--209.

\bibitem{li2014symbolic}
\selectlanguageifdefined{english}
\textit{Symbolic optimization with SMT solvers}~/ Yi~Li, Aws~Albarghouthi,
  Zachary~Kincaid et~al.~// ACM SIGPLAN Notices~/ ACM. \BibDash
\newblock Vol.~49. \BibDash
\newblock 2014. \BibDash
\newblock P.~607--618.

\bibitem{sharma2018veritesting}
\selectlanguageifdefined{english}
\textit{Veritesting Challenges in Symbolic Execution of Java}~/ Vaibhav~Sharma,
  Michael~W~Whalen, Stephen~McCamant, Willem~Visser~// \BibEmph{ACM SIGSOFT
  Software Engineering Notes}. \BibDash
\newblock 2018. \BibDash
\newblock Vol.~42, no.~4. \BibDash
\newblock P.~1--5.

\bibitem{mandrik}
\selectlanguageifdefined{russian}
\BibEmph{Мандрыкин~Михаил~Усамович}.
  Моделирование памяти Си-программ для
  инструментов статической верификации на
  основе SMT-решателей~: Ph.\,D. thesis~/
  Михаил~Усамович~Мандрыкин~; Диссертация
  на соискание ученой степени кандидата
  физико-математических наук ИСП РАН,
  Москва. \BibDash
\newblock 2016.

\end{thebibliography}
