\begin{thebibliography}{10}
\def\selectlanguageifdefined#1{
\expandafter\ifx\csname date#1\endcsname\relax
\else\selectlanguage{#1}\fi}
\providecommand*{\href}[2]{{\small #2}}
\providecommand*{\url}[1]{{\small #1}}
\providecommand*{\BibUrl}[1]{\url{#1}}
\providecommand{\BibAnnote}[1]{}
\providecommand*{\BibEmph}[1]{#1}
\ProvideTextCommandDefault{\cyrdash}{\iflanguage{russian}{\hbox
  to.8em{--\hss--}}{\textemdash}}
\providecommand*{\BibDash}{\ifdim\lastskip>0pt\unskip\nobreak\hskip.2em plus
  0.1em\fi
\cyrdash\hskip.2em plus 0.1em\ignorespaces}
\renewcommand{\newblock}{\ignorespaces}

\bibitem{Baruah2003DynamicAS}
\selectlanguageifdefined{english}
\BibEmph{Baruah~S.~K.} Dynamic- and Static-priority Scheduling of Recurring
  Real-time Tasks~// \BibEmph{Real-Time Systems}. \BibDash
\newblock 2003. \BibDash
\newblock P.~93--128.

\bibitem{Baruah2006SustainableSA}
\selectlanguageifdefined{english}
\BibEmph{Baruah~S.~K., Burns~A.} Sustainable Scheduling Analysis~//
  \BibEmph{2006 27th IEEE International Real-Time Systems Symposium (RTSS'06)}.
  \BibDash
\newblock 2006. \BibDash
\newblock P.~159--168.

\bibitem{Becker2001ExecutionEF}
\selectlanguageifdefined{english}
\BibEmph{Becker~L.~B.} Execution Environment for Dynamically Scheduling
  Real-Time Tasks. \BibDash
\newblock 2001.

\bibitem{Bertogna2011ImprovingFO}
\selectlanguageifdefined{english}
\BibEmph{Bertogna~M., Buttazzo~G.~C., Yao~G.} Improving Feasibility of Fixed
  Priority Tasks Using Non-Preemptive Regions~// \BibEmph{2011 IEEE 32nd
  Real-Time Systems Symposium}. \BibDash
\newblock 2011. \BibDash
\newblock P.~251--260.

\bibitem{Bertogna2005ImprovedSA}
\selectlanguageifdefined{english}
\BibEmph{Bertogna~M., Cirinei~M., Lipari~G.} Improved schedulability analysis
  of EDF on multiprocessor platforms~// \BibEmph{17th Euromicro Conference on
  Real-Time Systems (ECRTS'05)}. \BibDash
\newblock 2005. \BibDash
\newblock P.~209--218.

\bibitem{Bril06messageresponse}
\selectlanguageifdefined{english}
\BibEmph{Bril~R.~J., Lukkien~J.~J., Davis~R.~I.} Message response time analysis
  for ideal controller area network (CAN) refuted~// In (to appear) Proc. 5th
  International Workshop on Real Time Networks (RTN. \BibDash
\newblock 2006.

\bibitem{Buttazzo2003RateMV}
\selectlanguageifdefined{english}
\BibEmph{Buttazzo~G.~C.} Rate Monotonic vs. EDF: Judgment Day~//
  \BibEmph{Real-Time Systems}. \BibDash
\newblock 2003. \BibDash
\newblock Vol.~29. \BibDash
\newblock P.~5--26.

\bibitem{Campoy2004SchedulabilityAI}
\selectlanguageifdefined{english}
\BibEmph{Campoy~A.~M., S{\'a}ez~S., Perles~A.} Schedulability analisys in EDF
  scheduler with cache memories. \BibDash
\newblock 2004.

\bibitem{Davis1993SchedulingST}
\selectlanguageifdefined{english}
\BibEmph{Davis~R.~I., Tindell~K., Burns~A.} Scheduling slack time in fixed
  priority pre-emptive systems~// RTSS. \BibDash
\newblock 1993.

\bibitem{Dhall}
\selectlanguageifdefined{english}
\BibEmph{Dhall~S.~K., Liu~C.~L.} On a Real-Time Scheduling Problem~//
  \href{http://dx.doi.org/10.1287/opre.26.1.127}{\BibEmph{Oper. Res.}} \BibDash
\newblock 1978. \BibDash
\newblock Vol.~26. \BibDash
\newblock P.~127--140.

\bibitem{gonthier:1}
\selectlanguageifdefined{english}
\BibEmph{Gonthier~G.} A computer-checked proof of the Four Colour Theorem.
  \BibDash
\newblock 2005.

\bibitem{Grolleau2007TutorialOR}
\selectlanguageifdefined{english}
\BibEmph{Grolleau~E.} Tutorial on real-time scheduling. \BibDash
\newblock 2007.

\bibitem{Guo2015EDFSA}
\selectlanguageifdefined{english}
\BibEmph{Guo~Z., Santinelli~L., Yang~K.} EDF Schedulability Analysis on
  Mixed-Criticality Systems with Permitted Failure Probability~// \BibEmph{2015
  IEEE 21st International Conference on Embedded and Real-Time Computing
  Systems and Applications}. \BibDash
\newblock 2015. \BibDash
\newblock P.~187--196.

\bibitem{Harbour2003ResponseTA}
\selectlanguageifdefined{english}
\BibEmph{Harbour~M.~G., Palencia~J.~C.} Response Time Analysis for Tasks
  Scheduled under EDF within Fixed Priorities~// RTSS. \BibDash
\newblock 2003.

\bibitem{Audsley1991HardRS}
\selectlanguageifdefined{english}
Hard Real-Time Scheduling: The Deadline-Monotonic Approach~/ N.~C.~Audsley,
  A.~Burns, M.~F.~Richardson, A.~J.~Wellings~// \BibEmph{IFAC Proceedings
  Volumes}. \BibDash
\newblock 1991. \BibDash
\newblock Vol.~24, no.~2. \BibDash
\newblock P.~127--132.

\bibitem{Jeffay1991OnNS}
\selectlanguageifdefined{english}
\BibEmph{Jeffay~K., Stanat~D.~F., Martel~C.~U.} On Non-Preemptive Scheduling of
  Periodic and Sporadic Tasks. \BibDash
\newblock 1991.

\bibitem{Joseph1986FindingRT}
\selectlanguageifdefined{english}
\BibEmph{Joseph~M., Pandya~P.~K.} Finding Response Times in a Real-Time
  System~// \BibEmph{Comput. J.} \BibDash
\newblock 1986. \BibDash
\newblock Vol.~29. \BibDash
\newblock P.~390--395.

\bibitem{Kwok1999StaticSA}
\selectlanguageifdefined{english}
\BibEmph{Kwok~Y.-K., Ahmad~I.} Static scheduling algorithms for allocating
  directed task graphs to multiprocessors~// \BibEmph{ACM Comput. Surv.}
  \BibDash
\newblock 1999. \BibDash
\newblock Vol.~31. \BibDash
\newblock P.~406--471.

\bibitem{lakshmanan:1}
\selectlanguageifdefined{english}
\BibEmph{Lakshmanan~K., Rajkumar~R.} Scheduling self-suspending real-time tasks
  with rate-monotonic priorities~// 16th Real-Time and Embedded Technology and
  Applications Symposium (RTAS’10). \BibDash
\newblock 2010.

\bibitem{Lehoczky1990FixedPS}
\selectlanguageifdefined{english}
\BibEmph{Lehoczky~J.~P.} Fixed Priority Scheduling of Periodic Task Sets with
  Arbitrary Deadlines~// RTSS. \BibDash
\newblock 1990.

\bibitem{Lehoczky1989TheRM}
\selectlanguageifdefined{english}
\BibEmph{Lehoczky~J.~P., Sha~L., Ding~Y.} The Rate Monotonic Scheduling
  Algorithm: Exact Characterization and Average Case Behavior~// RTSS. \BibDash
\newblock 1989.

\bibitem{leroy}
\selectlanguageifdefined{english}
\BibEmph{Leroy~X.} Formal verification of a realistic compiler~//
  \BibEmph{Communications of the ACM}. \BibDash
\newblock 2009. \BibDash
\newblock Vol.~52, no.~7. \BibDash
\newblock P.~107--115.

\bibitem{LEUNG1982237}
\selectlanguageifdefined{english}
\BibEmph{Leung~J. Y.-T., Whitehead~J.} On the complexity of fixed-priority
  scheduling of periodic, real-time tasks~// \BibEmph{Performance Evaluation}.
  \BibDash
\newblock 1982. \BibDash
\newblock Vol.~2, no.~4. \BibDash
\newblock P.~237--250.

\bibitem{Liu1973SchedulingAF}
\selectlanguageifdefined{english}
\BibEmph{Liu~C.~L., Layland~J.~W.} Scheduling Algorithms for Multiprogramming
  in a Hard-Real-Time Environment~// \BibEmph{J. ACM}. \BibDash
\newblock 1973. \BibDash
\newblock Vol.~20. \BibDash
\newblock P.~46--61.

\bibitem{chen}
\selectlanguageifdefined{english}
Many suspensions, many problems: A review of self-suspending tasks in real-time
  systems~: Rep.~/ Department of Computer Science~; Executor: J.-J.~Chen,
  G.~Nelissen, W.-H.~Huang et~al.~: 2016.

\bibitem{Sakellariou2007SchedulingWW}
\selectlanguageifdefined{english}
Scheduling Workflows with Budget Constraints~/ R.~Sakellariou, H.~Zhao,
  E.~Tsiakkouri, M.~D.~Dikaiakos. \BibDash
\newblock 2007.

\bibitem{Short2010ImprovedTM}
\selectlanguageifdefined{english}
\BibEmph{Short~M.} Improved Task Management Techniques for Enforcing EDF
  Scheduling on Recurring Tasks~// \BibEmph{2010 16th IEEE Real-Time and
  Embedded Technology and Applications Symposium}. \BibDash
\newblock 2010. \BibDash
\newblock P.~56--65.

\bibitem{Spuri1996SchedulingAT}
\selectlanguageifdefined{english}
\BibEmph{Spuri~M., Buttazzo~G.~C.} Scheduling aperiodic tasks in dynamic
  priority systems~// \BibEmph{Real-Time Systems}. \BibDash
\newblock 1996. \BibDash
\newblock P.~179--210.

\bibitem{nelissen}
\selectlanguageifdefined{english}
Timing analysis of fixed priority self-suspending sporadic tasks~/ G.~Nelissen,
  J.~Fonseca, G.~Raravi, V.~Nelis~// 27th Euromicro Conference on Real-Time
  Systems (ECRTS’15). \BibDash
\newblock 2015.

\bibitem{Tindell1994AnEA}
\selectlanguageifdefined{english}
\BibEmph{Tindell~K., Burns~A., Wellings~A.~J.} An extendible approach for
  analyzing fixed priority hard real-time tasks~// \BibEmph{Real-Time Systems}.
  \BibDash
\newblock 1994. \BibDash
\newblock Vol.~6. \BibDash
\newblock P.~133--151.

\bibitem{chen:2}
\selectlanguageifdefined{english}
Using Crash Hoare logic for certifying the FSCQ file system~/ H.~Chen,
  D.~Ziegler, T.~Chajed et~al.~// 25th Symposium on Operating Systems
  Principles (SOSP’15). \BibDash
\newblock 2015. \BibDash
\newblock P.~18--37.

\bibitem{Wang1999SchedulingFT}
\selectlanguageifdefined{english}
\BibEmph{Wang~Y., Saksena~M.} Scheduling Fixed-Priority Tasks with Preemption
  Threshold~// RTCSA. \BibDash
\newblock 1999.

\bibitem{Zhang2009SchedulabilityAF}
\selectlanguageifdefined{english}
\BibEmph{Zhang~F., Burns~A.} Schedulability Analysis for Real-Time Systems with
  EDF Scheduling~// \BibEmph{IEEE Transactions on Computers}. \BibDash
\newblock 2009. \BibDash
\newblock Vol.~58. \BibDash
\newblock P.~1250--1258.

\bibitem{gonthier:2}
\selectlanguageifdefined{english}
A machine-checked proof of the Odd Order Theorem~/ G.~Gonthier, A.~Asperti,
  J.~Avigad et~al.~// 4th International Conference on Interactive Theorem
  Proving (ITP’13). \BibDash
\newblock 2013.

\bibitem{klein}
\selectlanguageifdefined{english}
seL4: Formal verification of an OS kernel~/ G.~Klein, K.~Elphinstone, G.~Heiser
  et~al.~// 22nd Symposium on Operating Systems Principles (SOSP’09).
  \BibDash
\newblock 2009. \BibDash
\newblock P.~207--220.

\bibitem{Coq}
\selectlanguageifdefined{english}
Coq prject. \BibDash
\newblock Access mode: \BibUrl{https://coq.inria.fr}.

\bibitem{Prosa}
\selectlanguageifdefined{english}
Prosa project. \BibDash
\newblock Access mode: \BibUrl{https://prosa.mpi-sws.org}.

\end{thebibliography}
