\begin{thebibliography}{1}
\def\selectlanguageifdefined#1{
\expandafter\ifx\csname date#1\endcsname\relax
\else\selectlanguage{#1}\fi}
\providecommand*{\href}[2]{{\small #2}}
\providecommand*{\url}[1]{{\small #1}}
\providecommand*{\BibUrl}[1]{\url{#1}}
\providecommand{\BibAnnote}[1]{}
\providecommand*{\BibEmph}[1]{#1}
\ProvideTextCommandDefault{\cyrdash}{\iflanguage{russian}{\hbox
  to.8em{--\hss--}}{\textemdash}}
\providecommand*{\BibDash}{\ifdim\lastskip>0pt\unskip\nobreak\hskip.2em plus
  0.1em\fi
\cyrdash\hskip.2em plus 0.1em\ignorespaces}
\renewcommand{\newblock}{\ignorespaces}

\bibitem{kuznetsov2012efficient}
\selectlanguageifdefined{english}
Efficient state merging in symbolic execution~/ Volodymyr~Kuznetsov,
  Johannes~Kinder, Stefan~Bucur, George~Candea~// \BibEmph{Acm Sigplan
  Notices}. \BibDash
\newblock 2012. \BibDash
\newblock Vol.~47, no.~6. \BibDash
\newblock P.~193--204.

\bibitem{godefroid2007compositional}
\selectlanguageifdefined{english}
\BibEmph{Godefroid~Patrice}. Compositional dynamic test generation~// ACM
  Sigplan Notices~/ ACM. \BibDash
\newblock Vol.~42. \BibDash
\newblock 2007. \BibDash
\newblock P.~47--54.

\bibitem{king1976symbolic}
\selectlanguageifdefined{english}
\BibEmph{King~James~C}. Symbolic execution and program testing~//
  \BibEmph{Communications of the ACM}. \BibDash
\newblock 1976. \BibDash
\newblock Vol.~19, no.~7. \BibDash
\newblock P.~385--394.

\bibitem{mcmillan2010lazy}
\selectlanguageifdefined{english}
\BibEmph{McMillan~Kenneth~L}. Lazy annotation for program testing and
  verification~// International Conference on Computer Aided Verification~/
  Springer. \BibDash
\newblock 2010. \BibDash
\newblock P.~104--118.

\bibitem{jaffar2012tracer}
\selectlanguageifdefined{english}
TRACER: A symbolic execution tool for verification~/ Joxan~Jaffar,
  Vijayaraghavan~Murali, Jorge~A~Navas, Andrew~E~Santosa~// International
  Conference on Computer Aided Verification~/ Springer. \BibDash
\newblock 2012. \BibDash
\newblock P.~758--766.

\bibitem{baldoni2018survey}
\selectlanguageifdefined{english}
A survey of symbolic execution techniques~/ Roberto~Baldoni, Emilio~Coppa,
  Daniele~Cono~D’elia et~al.~// \BibEmph{ACM Computing Surveys (CSUR)}.
  \BibDash
\newblock 2018. \BibDash
\newblock Vol.~51, no.~3. \BibDash
\newblock P.~50.

\end{thebibliography}
